### 2014-09-29 paper.tex
Initial commit: ROMAN paper

\documentclass{sig-alternate}

% UTF8 support
\usepackage[utf8x]{inputenc}

\usepackage{subfig}
\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{{figures/}}

\usepackage{booktabs}

\newcommand{\eg}{{\textit{e.g.~}}}
\newcommand{\etal}{{\textit{et al.~}}}
\newcommand{\ie}{{\textit{i.e.~}}}

%
% --- Author Metadata here ---
\conferenceinfo{10th ACM/IEEE International Conference on Human-Robot Interaction}{2015 Portland, USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{\LARGE \bf
    Eye tracking with Educational Robots: A Cautionary Tale
}

%%% HRI 2015 -> double-blind review process

%\numberofauthors{1} 
%\author{
%\alignauthor
%Julia Fink, S\'{e}verin Lemaignan, Pierre Dillenbourg\\
%%\titlenote{Dr.~Trovato insisted his name be first.}
%       \affaddr{Computer-Human Interaction in Learning and Instruction Lab (CHILI)}\\
%       \affaddr{Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL)}\\
%       \affaddr{CH-1015 Lausanne}\\
%       \affaddr{Switzerland}\\
%       \email{firstname.lastname@epfl.ch}
%}
%
%\additionalauthors{Additional authors: 
%Francesco Mondada, LSRO, EPFL, francesco.mondada@epfl.ch 
%}
%

\begin{document}
\maketitle
\begin{abstract}

We present an eye-tracking study on an educational robot
Thymio II with 52 participants. The participants observed the robot
detecting obstacles in the first phase of the experiment and they
interacted with the robot in the second phase of the experiment.
Finally, they were asked to explain the functionality of the robot. The
gaze of the participants was recorded during both the phases. The values
from the robot's sensors were visualized on the robot's body using LEDs
in two different ways in the two experimental conditions and there was
no sensor data visualization in the control condition. We found that the
sensor data visualization has an impact on the gaze patterns and the
performance of the participants. The main goal of the experiment was to
investigate that eye tracking could bring insights to the effectiveness
of the interaction between the human user and the robot.

\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Eye tracking provides unprecedented access to the users' attention and
engagement during interactive scenarios. Previous research has shown
that gaze data can be used as a proxy to understand the underlying
socio-cognitive aspects in not only human-computer interaction but in
human-human interaction as well. In the present decade, off the shelf
eye-trackers have become readily available to the researchers to assess
the users' attention and engagement.

On the other hand, educational robots can be of great use in making
young school kids interested in technological developments
~\cite{2, 17}. It is important to know about the key socio-cognitive
features of this subset of human-robot interaction because these
features let the researchers design better interactive scenarios in the
future. These features include the conceptual mapping of the sensor data
visualization and the robot's function and the generalizing the concepts
to solve a given problem in a contextual learning environment. ~

Thymio II~\cite{10} can provide salient effects onto our visual attention
through the LEDs. We can use this feature to guide the users' attention
in a way that the effectiveness of the interaction is maximized. In the
case of interaction with the educational robots the effect of the
interaction is to make the users understand the technical aspects of the
robot and to make the users be able to transfer it to different domains.

We present a study with combining eye tracking and human robot
interaction (HRI) in an educational setting. ~Eye tracking data is of
high temporal precision as compared to some of the physiological data
sources such as fMRI or other biometric devices used to measure the
palpitation and the body temperature. The eye tracking devices are
portable enough as opposed to the bulky apparatus used in fMRI~\cite{9}.
Eye tracking data provides more direct access to the users' attention
than other portable and physiological data sources such as EEG; this
makes eye-tracking data a pertinent source to measure attention.

Evaluation of HRI is mostly done through qualitative questionnaires and
qualitative data (interaction videos, interviews for example). The
physiological measurements such as eye tracking being precise, pertinent
and portable at the same time provides an added value to the researcher.
However, this needs to be complemented with the qualitative data as
well.

We propose to use the mobile eye trackers to be able to have our
participants freely move on the experiment site. Using mobile eye
tracker poses a technical challenge to automatically locate where the
participants are looking. This is not a trivial task as the visual
stimulus for participants is changing with every bit of motion of their
head. This is the reason we used fiducial-markers on the maze we used in
the experiment so that we can reconstruct the whole maze even if only a
part of it is the visual field of the participant.

Our working hypothesis is that with careful mapping between the LED
visualizations and the behavior of the robot we can induce the
understanding of the functionality of the robot very easily. We propose
to use the gaze data to verify this hypothesis. With eye-tracking data
we can judge whether the mapping between the behavior and visual
actuators is useful or not for the participants' understanding.
Moreover, we hypothesize that the good performers will be able to
anticipate the robot's motion. Eye-tracking data can also be useful to
verify the anticipation hypothesis. ~

The experiment consists in two phases. The first phase is the
observation phase during which the participants watch the robot move and
detect an obstacle in a ``playground''. The second phase requires the
participants to interact with the robot by placing an obstacle in its
path to make it detect the obstacle before reaching a certain target.
After each phase the participant explain the behavior of the robot. The
sensor data was visualized through LEDs with three visualization
conditions: TRUE visualization, RANDOM visualization and NONE
visualization. Through this experiment we investigate the following
research questions:

\begin{enumerate}
    \item Are there different gaze patterns for different levels of performance
during the interaction? Moreover, can we see any anticipation patterns
for the good performers?

    \item How does displaying the sensor information on the robot' body as a
visual cue affects the gaze and performance of the participants?
\end{enumerate}

The rest of the paper is organized as follows. The second section gives
a brief review of the eye-tracking research done to quantify the
expertise and performance. The third section presents the specificities
of the study. The fourth section lists the main results. The fifth
section discusses the results. Finally, the sixth section concludes the
paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Related Work: Gaze patterns and Expertise/Task based performance}

Several scholars related gaze patterns with level of expertise. \cite{4}
in an air traffic-monitoring task found out that the experts looked less
at the scenario-specific information than novices.
\cite{3, 7, 16} studied the effect of expertise on the gaze
patterns in different surgical tasks and concluded that experts look
less at the instruments than the novices, instead they focus more on the
task specific areas. \cite{11} showed that expert chess players pay more
attention to the relative positions of the pieces, rather than the
individual pieces, than novice chess players. \cite{1} also studied the
difference between experts and novice chess players in a checkmate
avoidance task and concluded that the experts have more gaze falling on
the important squares than the novices. In a program-debugging task, \cite{12} showed that the expert programmers scan through all the lines
in the program faster than the novices. In a collaborative Tetris game,
\cite{5} showed that experts pay more attention to the stack of
Tetronimoes while novices allocate more attention to the new pieces
falling from the top.

Our previous work also show a clear relation between gaze patterns and
task-based performance. In a pair-programming task, \cite{6} showed that
the good performing pairs have more synchronized gaze on different parts
of a program than the bad performing pairs. In a similar task, \cite{13}
showed that the good performing pairs pay more attention to the
data-flow of the program than the poor performing pairs. Moreover,
\cite{14} showed that while describing the functionality of a program the
well performing teams had more gaze on the variable modification parts
in the program while poor performing teams have equal distribution of
gaze on different parts of the program during similar phase of the task.
Thus we see that previous research provides insights about the
relationship between the gaze patterns and the behavioral and task-based
performance indicators in diverse scenarios.

It must be noted that to our best knowledge only very few studies have
investigated how eye-tracking could be used to assess HRI. In an
eye-tracking study, in the context of human robot interaction, \cite{15}
found that when the robot provides a matching visual and verbal
reference to an object the participants were more likely to look at the
correct objects. This result was consistent irrespectively of the
ambiguity of the situation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experiment}

\subsection{Setup and Conditions}

Thymio II is a small robot designed for education for 6 to 16 year old
children~\cite{8, 10}. Users can interact with it via buttons and
distance sensors. The robot can display its states via many LEDs and its
motion. We programmed it to show the value of the front IR-sensor on its
top. The display consists of 8 LEDs (Figure~\ref{thymio}).

~In the experiment, there were 3 sensor data visualization conditions.
~For the TRUE visualization condition, the number of illuminated LEDs,
on the top of the robot, is proportional to the intensity measured by
the IR-sensor. When the intensity of the reflected IR crosses a
predefined threshold, the robot does a 90° turn to its right. For the
two other conditions, the behavior is the same, simply the display
changes. In the RANDOM condition, the display shows as if the robot was
detecting the obstacle at random moments, while in the NONE
visualization condition nothing is shown on top of the robot. The robot
has a fitting for a pencil that we used for the drawing of its
trajectory.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{thymio}
    \caption{\small \textbf{Thymio II}: the proximity sensors were used to
    detect the obstacle based on the reflectance of the material. The sensor
    data was shown as a proportion of the circle lit using the LEDs on top of the
    robot.}

    \label{thymio}
\end{figure}

The playground (Figure~\ref{playground}) is designed in order to allow the
participants to get a reference of the previous behavior of the robot, as well
as to allow us to localize the position of the robot, the position of the
obstacles and the position of the gaze on the video recorded from the
eye-tracker. The localization is made possible by the use of unique fiducial
markers on the playground. On the right hand side, the observation phase takes
place and there will be the reference for the black and white obstacles. On the
left hand side, the interaction takes place.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{playground}
    \caption{\small Basic playground for the experiment. The fiducial markers
    are used for automatic localization of the gaze pointers on the observation
    video.}

    \label{playground}
\end{figure}

One important fact to be considered is that the localization of the
robot, the obstacle or the gaze pointer on the observation field for the
participant is not a trivial task. The fact that the participants are
free to move, poses a challenge to the eye-tracking analysis. The
movement of the participant causes change in the observation field of
the participant almost every frame of the eye-tracking video. To cope up
with the changing observation field we decided to put an array of
fiducial markers on the playground. Using the fiducial markers enabled
us to recreate the whole playground for every frame in the video
recorded from the eye-tracker's camera (Figure~\ref{expe}).

\subsection{Procedure}

Upon their arrival at the experiment site, the participants signed a
consent form and answered a small questionnaire about demographics and
participant's experience with educational robots (this we later consider
as expertise). The participants were placed in front of the playground
(Figure~\ref{expe}) and were equipped with the SMI eye-tracking glasses. The
actual experiment consisted in two phases: observation phase and
interaction phase.

\paragraph{Observation phase} The participant observes the Thymio II robot
approaching obstacles. The robot turns as soon as it detects the
obstacle. The participant watches the robot's behavior for a black and a
white obstacle for 5 trials each. For the white, the robot turns
earlier; for the black obstacle the robot turns later. In the final
trial the robot is equipped with a pen to draw its trajectory for both
obstacles with different colors. After drawing, the participant is asked
the question: ``How does the robot work?''

\paragraph{Interaction phase} In the second phase, the participant is asked
to guide the robot to a goal, using a gray obstacle. The participant can put the
obstacle wherever he likes on the left hand side (Figure~\ref{playground}) of
the playground before the robot starts. We designed the gray obstacle to reflect
more infrared light (IR) than the black or the white obstacles therefore the
robot turns even earlier. This leads to a surprising effect. The participant has
only the robot's trajectories as a source of information. Each participant is
given 5 trials to put the obstacle in order to guide the robot to the goal. The
participant then has to answer the same question as in the observation phase,
response to which is considered as a final answer.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{expe}
    \caption{\small Experimental setup for observation phase. The observation
    video is recorded from the video camer in the front of the eye tracker (in
    the lop-left corner).}

    \label{expe}
\end{figure}

\subsection{Participants}

We recruited 52 participants for the experiment. All of them were
students from École Polytechnique Fédérale de Lausanne, Switzerland.
Most of them were in their first year undergraduate program (with two
exceptions). ~The age distribution was narrow, with a mean of 19.7 and a
standard deviation of 1.97. There were 13 female and 39 male
participants. In the three experimental conditions, NONE, RANDOM and
TRUE, there were 18, 17 and 17 participants respectively.

\subsection{Performance measures}

We had two measures of performance. First measure was a rating given to
the responses that participants gave to the question about the
functionality of the robot. Second measure was the distance from the
target in the interaction phase.

We transcribed the responses to perform a rating scheme on the level of
abstraction and correctness. A low level of abstraction consists in
describing the functionality of the robot in the terms of the electric
or programming aspects of the robot, a high level represents describing
the behavior. For the levels of correctness, we categorized the
responses into correct or incorrect response. In TABLE I. we present
sample responses for the different categories.

\begin{table}[ht!]
    \centering
    \footnotesize
    \begin{tabular}{ccp{4.5cm}}
        \toprule
        Correct. & Abstract. & Sample answer \\
        \midrule
        \textit{incorrect} & \textit{low} & ``The robot turns at a given distance in respect to a color, defined in the program.''\\ 
        \midrule
        \textit{incorrect} & \textit{high} & `Gray is the most dangerous, so the
        robot turn really early.''\\ 
        \midrule
        \textit{correct} & \textit{low} & ``The gray obstacle reflects a lot,
        the robot sends light. At a certain threshold the robot turns.'' \\ 
        \midrule
        \textit{correct} & \textit{high} & ``The gray obstacle is shinier, so
        more reflective, and better detectable.''\\ 
        \bottomrule
    \end{tabular}
    \caption{Sample answers for all classes}

    \label{sample_answer}
\end{table}

Second, the distances from the target were measured for all 5 trials. As
a matter of fact, as soon as the principle of the robot was deemed to be
understood by the participants, almost all the participants behaved the
same way. On the first try almost every participant failed and the robot
turned instantly. So the most significant distance measure was the
improvement between the first and second trial. It is referred to as
improvement in the following sections.

Incorrect answers were further classified into 4 categories; we present
each category accompanied by a sample response:

\begin{itemize}
    \item The participant did not respond or offer a possible explanation: ``I
        really don't know how the robot works''.

    \item The participant identified a wrong cause for the behavior of the robot:
        ``The robot notices the tags on the side''.

    \item The participant held the code responsible for the cause of different
        behavior: ``The robot turns at a given distance in respect to a color,
        defined in the program''.

    \item The participant tried to explain by analogies or did not explain the
        robots behavior at an understandable level: ``Gray is the most
        dangerous, so the robot turns really early''.

\end{itemize}

\subsection{Gaze measures}

The most common form of eye-tracking data aggregation are the fixations.
Fixations depict the periods in the user's observation when the user
attends a relatively small part of the visual stimulus for a relatively
longer period of time. The various fixation detection algorithms are
summarized in~\cite{18}. Following are the two gaze measures, derived
from the fixations, which we used in the present work.

Average fixation duration on the robot: We measured the amount of time a
participant looks at the robot and averaged this duration for the number
of fixations on the robot for the particular participant.

Average fixation on the reference side: The main area (right hand side
of figure 2) in the observation phase is treated as the reference side
in the interaction phase. The rationale behind keeping the lines drawn
by the robot in the observation phase is for the participants to be able
to refer to the prior behavior of the robot in the interaction phase. We
measured the amount of time a participant looks at the reference side
and averaged this duration for the number of fixations on the reference
side for the particular participant.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results}

We found no bias for age, gender, expertise, student status or condition
in respect to the correctness, abstraction and type of mistake made for
the final answer. Surprisingly there is no correlation between the
visualization condition and the correctness or abstraction of the
answers given. We could not find any anticipation patterns in the
eye-tracking data. We found some other relation between the different
measures. We present the results in following subsections.

\subsection{Average fixation duration on the robot during observation phase
vs.~condition}

The average fixation duration on the robot during observation phase
(Figure~\ref{res1}) is significantly more in TRUE and RANDOM condition than in
the NONE condition ($F[2,49]=3.68$, p = .03). This depicts that the
sensor data visualization has an effect on the users' attention.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{res1}
    \caption{Average fixation duration on the robot ~during the observation phase
    vs.~Condition}
    \label{res1}
\end{figure}

\subsection{First improvement vs.~condition}

The first improvement is significantly more in NONE and RANDOM
conditions (Figure~\ref{res2}) than in the TRUE condition ($F[2,49]=3.75$, p =
0.03).

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{res2}
    \caption{First improvement vs.~experimental condition}
    \label{res2}
\end{figure}

\subsection{Average fixation duration on the reference side during interaction
phase vs.~condition}

The average fixation time on the reference side of the playground
(Figure~\ref{res3}) during the interaction phase is significantly more in NONE
and RANDOM condition than it is in the TRUE condition ($F[2,49]=4.19$,
p = .02).

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{res3}
    \caption{Average fixation duration on the reference side during the
    interaction phase vs.~Condition}
    \label{res3}
\end{figure}

\subsection{First improvement vs number of fixations on reference side}

There is a significant negative correlation between the number of
fixations on the reference side (Figure~\ref{res4}) during the interaction phase
and the first Improvement ($t(50)=-2.13$, Pearson's correlation = -0.29, p=.03).

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{res4}
    \caption{First improvement in centimeters ($y$-axis) vs.~number of fixations
    on reference side ($x$-axis) during the interaction phase.}
    \label{res4}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}

We present an eye-tracking study in the context of human-robot
interaction with an educational setting. The fact that participants have
higher average fixation duration on the robot during the observation
phase in the NONE condition than the other two conditions (Figure 4) is
not surprising as displaying visual information on the robot induces a
saliency effect on the attention and the gaze is attracted towards the
salient feature in the field of view.

The fact that the participants in the RANDOM or NONE visualization
condition improved more than those with TRUE condition is surprising
(Figure 5). There are two plausible explanations. The first is that
participants who see the robot in the TRUE condition have a stronger
believe that the robot always behaves the same. They see the LEDs of the
robot turning on and therefore the robot still works. The ones with NONE
visualization do not have an indication whether the robot works the same
way as in the observation phase, and start experimenting earlier. The
second is that the participants in TRUE condition just put the obstacles
out of detection range, because they could see different display
information and concluded therefore it may behave differently.

The fact that participants have lower average fixation duration on the
reference side in the interaction phase in the TRUE condition than the
other two conditions actually supports the explanation that participants
with TRUE condition had a higher initial belief in their cognitive model
of how does the robot work (Figure 6). They did not need to look onto
the reference given in observation phase. This also verifies our working
hypothesis that a carefully designed mapping between the robot's
behavior and its visual actuators can help in maximizing the learning
effect during the interaction.

We demonstrated that eye-tracking data can provide several process
variables to assess not only the task-based performance of the
participants but also to evaluate HRI. The prime advantage of using
mobile eye-tracking is that the users' interaction with the robot can
still be ecologically valid. On the other hand, using fMRI for
evaluating HRI reduces the interaction to a video of the robot only
~\cite{9}.

Another advantage of using mobile eye-tracking to evaluate HRI,
especially in an educational context, is that the data provides direct
and noise free access to the users' attention. While in other
physiological measures for attention, such as EEG, the data has a lot of
noise and the relation to the attention is very task-specific.

The advantages of mobile eye-tracking come with an additional cost. As
we mentioned earlier, the automatic localization of the gaze pointer on
the visual stimulus is not a trivial task. To do this we have to use a
number of fiducial markers to the playground (Figure 2). We observed
that the fiducial markers cause a distraction to the participants. As a
future work, we are trying to find a suitable replacement to the
fiducial markers.

Another plausible explanation for the participants in NONE and RANDOM condition
being better performers than the TRUE condition during the interaction phase
comes from the transparency of the robot's behavior~\cite{20}. The robot's
behavior was not at all transparent in the former two conditions. This might
have caused the participants to put more effort in understanding the behavior.
Therefore, they performed better.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

Our effort to use the confluent of eye tracking and human-robot
interaction provides insights to two aspects: first, as a way to
evaluate the human-robot interaction and second, as a way to evaluate
the interaction scenario.

We addressed two research questions in the beginning of the present
work. The results show that the way the sensor data is visualized has an
impact on both the gaze patterns and the performance (Question 2).
However, for the relation between the gaze patterns of the participants
and their performance outcomes (Question 1) we cannot claim a direct
relation. We found a negative correlation between the gaze-patterns and
the first improvement during the interaction phase. We could not find a
relation between the explanation of the participants and their
gaze-patterns. Moreover, we did not find any anticipation patterns in
the gaze data. The lack of evidence for the relation between
participants' explanations and their gaze patterns prevents us to make
any strong claims about the relation between the overall performance and
the gaze patterns.

The fact that we cannot find a relation between the gaze patterns and
all the factors in the performance might have its roots in the way we
designed the interaction phase experiment. As a working hypothesis we
said that there should be clear and carefully designed mapping between
the robots' behavior and the sensor data visualization. Its environment
also affects the behavior of the robot and hence the environment also
should be taken into consideration while designing the
behavior-visualization mapping. We introduced a novelty (the gray
obstacle being more reflective) in the environment during the
interaction phase of the experiment that forced the participants to
revise their hypothesis and hence they failed to understand the robot's
functionality. This also serves as a word of caution in future while
designing such interactions. The observation phase serves as a training
session for the participants, which can later be tested during the
interaction phase. Any novel behavior modality (in our case, the more
reflective gray obstacle) can have a negative impact on the
participants' understanding.

In a nutshell, the use of gaze data as an assessment of the human-robot
interaction in an educational setting provides future research
prospects. The data acquisition is a better trade-off between the
ecological validity of the experiment (as there cannot be an interaction
with the robot fMRI data acquisition) and the precision of the data
stream (wristbands for measuring the palpitation and the temperature).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}

This research was supported by...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{abbrv}
\bibliography{eyetracking}

\balancecolumns

\end{document}

### 2014-09-29 paper.tex
Added biblio. 2 entries are missing

@@
 
-On the other hand, educational robots can be of great use in making
-young school kids interested in technological developments
-~\cite{2, 17}. It is important to know about the key socio-cognitive
-features of this subset of human-robot interaction because these
-features let the researchers design better interactive scenarios in the
-future. These features include the conceptual mapping of the sensor data
-visualization and the robot's function and the generalizing the concepts
-to solve a given problem in a contextual learning environment. ~
+On the other hand, educational robots can be of great use in making young school
+kids interested in technological developments~\cite{cooper1999robots,
+wyffels2010building}. It is important to know about the key socio-cognitive
+features of this subset of human-robot interaction because these features let
+the researchers design better interactive scenarios in the future. These
+features include the conceptual mapping of the sensor data visualization and the
+robot's function and the generalizing the concepts to solve a given problem in a
+contextual learning environment. ~
 
-Thymio II~\cite{10} can provide salient effects onto our visual attention
-through the LEDs. We can use this feature to guide the users' attention
-in a way that the effectiveness of the interaction is maximized. In the
-case of interaction with the educational robots the effect of the
-interaction is to make the users understand the technical aspects of the
-robot and to make the users be able to transfer it to different domains.
+Thymio II~\cite{riedo2012two} can provide salient effects onto our visual
+attention through the LEDs. We can use this feature to guide the users'
+attention in a way that the effectiveness of the interaction is maximized. In
+the case of interaction with the educational robots the effect of the
+interaction is to make the users understand the technical aspects of the robot
+and to make the users be able to transfer it to different domains.
 
-We present a study with combining eye tracking and human robot
-interaction (HRI) in an educational setting. ~Eye tracking data is of
-high temporal precision as compared to some of the physiological data
-sources such as fMRI or other biometric devices used to measure the
-palpitation and the body temperature. The eye tracking devices are
-portable enough as opposed to the bulky apparatus used in fMRI~\cite{9}.
-Eye tracking data provides more direct access to the users' attention
-than other portable and physiological data sources such as EEG; this
-makes eye-tracking data a pertinent source to measure attention.
+We present a study with combining eye tracking and human robot interaction (HRI)
+in an educational setting. ~Eye tracking data is of high temporal precision as
+compared to some of the physiological data sources such as fMRI or other
+biometric devices used to measure the palpitation and the body temperature. The
+eye tracking devices are portable enough as opposed to the bulky apparatus used
+in fMRI~\cite{rosenthal2013neural}.  Eye tracking data provides more direct
+access to the users' attention than other portable and physiological data
+sources such as EEG; this makes eye-tracking data a pertinent source to measure
+attention.
 
 Evaluation of HRI is mostly done through qualitative questionnaires and
-qualitative data (interaction videos, interviews for example). The
-physiological measurements such as eye tracking being precise, pertinent
-and portable at the same time provides an added value to the researcher.
-However, this needs to be complemented with the qualitative data as
-well.
+qualitative data (interaction videos, interviews for example). The physiological
+measurements such as eye tracking being precise, pertinent and portable at the
+same time provides an added value to the researcher.  However, this needs to be
+complemented with the qualitative data as well.
 
-We propose to use the mobile eye trackers to be able to have our
-participants freely move on the experiment site. Using mobile eye
-tracker poses a technical challenge to automatically locate where the
-participants are looking. This is not a trivial task as the visual
-stimulus for participants is changing with every bit of motion of their
-head. This is the reason we used fiducial-markers on the maze we used in
-the experiment so that we can reconstruct the whole maze even if only a
-part of it is the visual field of the participant.
+We propose to use the mobile eye trackers to be able to have our participants
+freely move on the experiment site. Using mobile eye tracker poses a technical
+challenge to automatically locate where the participants are looking. This is
+not a trivial task as the visual stimulus for participants is changing with
+every bit of motion of their head. This is the reason we used fiducial-markers
+on the maze we used in the experiment so that we can reconstruct the whole maze
+even if only a part of it is the visual field of the participant.
 
 Our working hypothesis is that with careful mapping between the LED
-visualizations and the behavior of the robot we can induce the
-understanding of the functionality of the robot very easily. We propose
-to use the gaze data to verify this hypothesis. With eye-tracking data
-we can judge whether the mapping between the behavior and visual
-actuators is useful or not for the participants' understanding.
-Moreover, we hypothesize that the good performers will be able to
-anticipate the robot's motion. Eye-tracking data can also be useful to
-verify the anticipation hypothesis. ~
+visualizations and the behavior of the robot we can induce the understanding of
+the functionality of the robot very easily. We propose to use the gaze data to
+verify this hypothesis. With eye-tracking data we can judge whether the mapping
+between the behavior and visual actuators is useful or not for the participants'
+understanding.  Moreover, we hypothesize that the good performers will be able
+to anticipate the robot's motion. Eye-tracking data can also be useful to verify
+the anticipation hypothesis.
 
-The experiment consists in two phases. The first phase is the
-observation phase during which the participants watch the robot move and
-detect an obstacle in a ``playground''. The second phase requires the
-participants to interact with the robot by placing an obstacle in its
-path to make it detect the obstacle before reaching a certain target.
-After each phase the participant explain the behavior of the robot. The
-sensor data was visualized through LEDs with three visualization
-conditions: TRUE visualization, RANDOM visualization and NONE
-visualization. Through this experiment we investigate the following
-research questions:
+The experiment consists in two phases. The first phase is the observation phase
+during which the participants watch the robot move and detect an obstacle in a
+``playground''. The second phase requires the participants to interact with the
+robot by placing an obstacle in its path to make it detect the obstacle before
+reaching a certain target.  After each phase the participant explain the
+behavior of the robot. The sensor data was visualized through LEDs with three
+visualization conditions: TRUE visualization, RANDOM visualization and NONE
+visualization. Through this experiment we investigate the following research
+questions:
 
@@
 
-Several scholars related gaze patterns with level of expertise. \cite{4}
-in an air traffic-monitoring task found out that the experts looked less
-at the scenario-specific information than novices.
-\cite{3, 7, 16} studied the effect of expertise on the gaze
-patterns in different surgical tasks and concluded that experts look
-less at the instruments than the novices, instead they focus more on the
-task specific areas. \cite{11} showed that expert chess players pay more
-attention to the relative positions of the pieces, rather than the
-individual pieces, than novice chess players. \cite{1} also studied the
-difference between experts and novice chess players in a checkmate
-avoidance task and concluded that the experts have more gaze falling on
-the important squares than the novices. In a program-debugging task, \cite{12} showed that the expert programmers scan through all the lines
-in the program faster than the novices. In a collaborative Tetris game,
-\cite{5} showed that experts pay more attention to the stack of
-Tetronimoes while novices allocate more attention to the new pieces
-falling from the top.
+Several scholars related gaze patterns with level of expertise.
+\cite{hasse2012measure} in an air traffic-monitoring task found out that the
+experts looked less at the scenario-specific information than novices.
+\cite{eivazi2012gaze, law2004eye, tien2010measuring} studied the effect of
+expertise on the gaze patterns in different surgical tasks and concluded that
+experts look less at the instruments than the novices, instead they focus more
+on the task specific areas. \cite{reingold2001visual} showed that expert chess
+players pay more attention to the relative positions of the pieces, rather than
+the individual pieces, than novice chess players. \cite{blignaut2008visual} also
+studied the difference between experts and novice chess players in a checkmate
+avoidance task and concluded that the experts have more gaze falling on the
+important squares than the novices. In a program-debugging task,
+\cite{sharif2012eye} showed that the expert programmers scan through all the
+lines in the program faster than the novices. In a collaborative Tetris game,
+\cite{jermann2010using} showed that experts pay more attention to the stack of
+Tetronimoes while novices allocate more attention to the new pieces falling from
+the top.
 
 Our previous work also show a clear relation between gaze patterns and
-task-based performance. In a pair-programming task, \cite{6} showed that
-the good performing pairs have more synchronized gaze on different parts
-of a program than the bad performing pairs. In a similar task, \cite{13}
-showed that the good performing pairs pay more attention to the
-data-flow of the program than the poor performing pairs. Moreover,
-\cite{14} showed that while describing the functionality of a program the
-well performing teams had more gaze on the variable modification parts
-in the program while poor performing teams have equal distribution of
-gaze on different parts of the program during similar phase of the task.
-Thus we see that previous research provides insights about the
-relationship between the gaze patterns and the behavioral and task-based
-performance indicators in diverse scenarios.
+task-based performance. In a pair-programming task, \cite{jermann2012effects}
+showed that the good performing pairs have more synchronized gaze on different
+parts of a program than the bad performing pairs. In a similar task,
+\cite{sharma2012gaze} showed that the good performing pairs pay more attention
+to the data-flow of the program than the poor performing pairs. Moreover,
+\cite{sharma2013understanding} showed that while describing the functionality of
+a program the well performing teams had more gaze on the variable modification
+parts in the program while poor performing teams have equal distribution of gaze
+on different parts of the program during similar phase of the task.  Thus we see
+that previous research provides insights about the relationship between the gaze
+patterns and the behavioral and task-based performance indicators in diverse
+scenarios.
 
 It must be noted that to our best knowledge only very few studies have
-investigated how eye-tracking could be used to assess HRI. In an
-eye-tracking study, in the context of human robot interaction, \cite{15}
-found that when the robot provides a matching visual and verbal
-reference to an object the participants were more likely to look at the
-correct objects. This result was consistent irrespectively of the
-ambiguity of the situation.
+investigated how eye-tracking could be used to assess HRI. In an eye-tracking
+study, in the context of human robot interaction, \cite{staudte2009visual} found
+that when the robot provides a matching visual and verbal reference to an object
+the participants were more likely to look at the correct objects. This result
+was consistent irrespectively of the ambiguity of the situation.
 
@@
 Thymio II is a small robot designed for education for 6 to 16 year old
-children~\cite{8, 10}. Users can interact with it via buttons and
-distance sensors. The robot can display its states via many LEDs and its
-motion. We programmed it to show the value of the front IR-sensor on its
-top. The display consists of 8 LEDs (Figure~\ref{thymio}).
+children~\cite{magnenat2012programming, riedo2012two}. Users can interact with
+it via buttons and distance sensors. The robot can display its states via many
+LEDs and its motion. We programmed it to show the value of the front IR-sensor
+on its top. The display consists of 8 LEDs (Figure~\ref{thymio}).
 
-~In the experiment, there were 3 sensor data visualization conditions.
-~For the TRUE visualization condition, the number of illuminated LEDs,
-on the top of the robot, is proportional to the intensity measured by
-the IR-sensor. When the intensity of the reflected IR crosses a
-predefined threshold, the robot does a 90° turn to its right. For the
-two other conditions, the behavior is the same, simply the display
-changes. In the RANDOM condition, the display shows as if the robot was
-detecting the obstacle at random moments, while in the NONE
-visualization condition nothing is shown on top of the robot. The robot
-has a fitting for a pencil that we used for the drawing of its
-trajectory.
+In the experiment, there were 3 sensor data visualization conditions.  For the
+TRUE visualization condition, the number of illuminated LEDs, on the top of the
+robot, is proportional to the intensity measured by the IR-sensor. When the
+intensity of the reflected IR crosses a predefined threshold, the robot does a
+90° turn to its right. For the two other conditions, the behavior is the same,
+simply the display changes. In the RANDOM condition, the display shows as if the
+robot was detecting the obstacle at random moments, while in the NONE
+visualization condition nothing is shown on top of the robot. The robot has a
+fitting for a pencil that we used for the drawing of its trajectory.
 
@@
 longer period of time. The various fixation detection algorithms are
-summarized in~\cite{18}. Following are the two gaze measures, derived
+summarized in~\cite{duchowski2007eye}. Following are the two gaze measures, derived
 from the fixations, which we used in the present work.
@@
 evaluating HRI reduces the interaction to a video of the robot only
-~\cite{9}.
+~\cite{rosenthal2013neural}.
 
@@
 being better performers than the TRUE condition during the interaction phase
-comes from the transparency of the robot's behavior~\cite{20}. The robot's
+comes from the transparency of the robot's behavior~\cite{??}. The robot's
 behavior was not at all transparent in the former two conditions. This might

### 2014-09-30 paper.tex
Figure updates and remove ref 20

@@
     \centering
-    \includegraphics[width=0.9\linewidth]{thymio}
+    \includegraphics[width=0.9\linewidth]{thymio0}
     \caption{\small \textbf{Thymio II}: the proximity sensors were used to
@@
     \centering
-    \includegraphics[width=0.9\linewidth]{playground}
+    \includegraphics[width=0.9\linewidth]{maze}
     \caption{\small Basic playground for the experiment. The fiducial markers
@@
     \centering
-    \includegraphics[width=0.9\linewidth]{expe}
+    \includegraphics[width=0.9\linewidth]{setup0}
     \caption{\small Experimental setup for observation phase. The observation
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{res1}
+    \includegraphics[width=0.8\linewidth]{meanPlotFixRobo.pdf}
     \caption{Average fixation duration on the robot ~during the observation phase
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{res2}
+    \includegraphics[width=0.8\linewidth]{meanPlotFirstImprove.pdf}
     \caption{First improvement vs.~experimental condition}
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{res3}
+    \includegraphics[width=0.8\linewidth]{meanPlotFixRreference.pdf}
     \caption{Average fixation duration on the reference side during the
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{res4}
+    \includegraphics[width=0.8\linewidth]{corPlotFirstImprove.pdf}
     \caption{First improvement in centimeters ($y$-axis) vs.~number of fixations
@@
 being better performers than the TRUE condition during the interaction phase
-comes from the transparency of the robot's behavior~\cite{??}. The robot's
+comes from the transparency of the robot's behavior. The robot's
 behavior was not at all transparent in the former two conditions. This might

### 2014-09-30 paper.tex
with previous commit
Removed old figures + temporary files
Updated figures (to a Latex style)
Updated author list (still hidden for review)
While here, hide the acknowledgment section as well
[formatting] Typeset conditions in sans serif

--- 2014-09-29 paper.tex
@@
 %\alignauthor
-%Julia Fink, S\'{e}verin Lemaignan, Pierre Dillenbourg\\
-%%\titlenote{Dr.~Trovato insisted his name be first.}
+%Kshitij Sharma, S\'{e}verin Lemaignan, Pierre Dillenbourg\\
 %       \affaddr{Computer-Human Interaction in Learning and Instruction Lab (CHILI)}\\
@@
 behavior of the robot. The sensor data was visualized through LEDs with three
-visualization conditions: TRUE visualization, RANDOM visualization and NONE
+visualization conditions: {\sf TRUE} visualization, {\sf RANDOM} visualization and {\sf NONE}
 visualization. Through this experiment we investigate the following research
@@
 In the experiment, there were 3 sensor data visualization conditions.  For the
-TRUE visualization condition, the number of illuminated LEDs, on the top of the
+{\sf TRUE} visualization condition, the number of illuminated LEDs, on the top of the
 robot, is proportional to the intensity measured by the IR-sensor. When the
@@
 90° turn to its right. For the two other conditions, the behavior is the same,
-simply the display changes. In the RANDOM condition, the display shows as if the
-robot was detecting the obstacle at random moments, while in the NONE
+simply the display changes. In the {\sf RANDOM} condition, the display shows as if the
+robot was detecting the obstacle at random moments, while in the {\sf NONE}
 visualization condition nothing is shown on top of the robot. The robot has a
@@
     \centering
-    \includegraphics[width=0.9\linewidth]{expe}
+    \includegraphics[width=0.9\linewidth]{setup}
     \caption{\small Experimental setup for observation phase. The observation
@@
 standard deviation of 1.97. There were 13 female and 39 male
-participants. In the three experimental conditions, NONE, RANDOM and
-TRUE, there were 18, 17 and 17 participants respectively.
+participants. In the three experimental conditions, {\sf NONE}, {\sf RANDOM} and
+{\sf TRUE}, there were 18, 17 and 17 participants respectively.
 
@@
 The average fixation duration on the robot during observation phase
-(Figure~\ref{res1}) is significantly more in TRUE and RANDOM condition than in
-the NONE condition ($F[2,49]=3.68$, p = .03). This depicts that the
+(Figure~\ref{res1}) is significantly more in {\sf TRUE} and {\sf RANDOM} condition than in
+the {\sf NONE} condition ($F[2,49]=3.68$, p = .03). This depicts that the
 sensor data visualization has an effect on the users' attention.
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{res1}
+    \includegraphics[width=0.8\linewidth]{meanPlotFixRobo}
     \caption{Average fixation duration on the robot ~during the observation phase
@@
 
-The first improvement is significantly more in NONE and RANDOM
-conditions (Figure~\ref{res2}) than in the TRUE condition ($F[2,49]=3.75$, p =
+The first improvement is significantly more in {\sf NONE} and {\sf RANDOM}
+conditions (Figure~\ref{res2}) than in the {\sf TRUE} condition ($F[2,49]=3.75$, p =
 0.03).
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{res2}
+    \includegraphics[width=0.8\linewidth]{meanPlotFirstImprove}
     \caption{First improvement vs.~experimental condition}
@@
 The average fixation time on the reference side of the playground
-(Figure~\ref{res3}) during the interaction phase is significantly more in NONE
-and RANDOM condition than it is in the TRUE condition ($F[2,49]=4.19$,
+(Figure~\ref{res3}) during the interaction phase is significantly more in {\sf NONE}
+and {\sf RANDOM} condition than it is in the {\sf TRUE} condition ($F[2,49]=4.19$,
 p = .02).
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{res3}
+    \includegraphics[width=0.8\linewidth]{meanPlotFixReference}
     \caption{Average fixation duration on the reference side during the
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{res4}
+    \includegraphics[width=0.8\linewidth]{corPlotFirstImprove}
     \caption{First improvement in centimeters ($y$-axis) vs.~number of fixations
@@
 higher average fixation duration on the robot during the observation
-phase in the NONE condition than the other two conditions (Figure 4) is
+phase in the {\sf NONE} condition than the other two conditions (Figure 4) is
 not surprising as displaying visual information on the robot induces a
@@
 
-The fact that the participants in the RANDOM or NONE visualization
-condition improved more than those with TRUE condition is surprising
+The fact that the participants in the {\sf RANDOM} or {\sf NONE} visualization
+condition improved more than those with {\sf TRUE} condition is surprising
 (Figure 5). There are two plausible explanations. The first is that
-participants who see the robot in the TRUE condition have a stronger
+participants who see the robot in the {\sf TRUE} condition have a stronger
 believe that the robot always behaves the same. They see the LEDs of the
-robot turning on and therefore the robot still works. The ones with NONE
+robot turning on and therefore the robot still works. The ones with {\sf NONE}
 visualization do not have an indication whether the robot works the same
 way as in the observation phase, and start experimenting earlier. The
-second is that the participants in TRUE condition just put the obstacles
+second is that the participants in {\sf TRUE} condition just put the obstacles
 out of detection range, because they could see different display
@@
 The fact that participants have lower average fixation duration on the
-reference side in the interaction phase in the TRUE condition than the
+reference side in the interaction phase in the {\sf TRUE} condition than the
 other two conditions actually supports the explanation that participants
-with TRUE condition had a higher initial belief in their cognitive model
+with {\sf TRUE} condition had a higher initial belief in their cognitive model
 of how does the robot work (Figure 6). They did not need to look onto
@@
 
-Another plausible explanation for the participants in NONE and RANDOM condition
-being better performers than the TRUE condition during the interaction phase
-comes from the transparency of the robot's behavior~\cite{??}. The robot's
+Another plausible explanation for the participants in {\sf NONE} and {\sf RANDOM} condition
+being better performers than the {\sf TRUE} condition during the interaction phase
+comes from the transparency of the robot's behavior. The robot's
 behavior was not at all transparent in the former two conditions. This might
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgments}
-
-This research was supported by...
+% Removed for double-blind review
+%\section*{Acknowledgments}
+%
+%This research was supported by...
 

### 2014-10-02 paper.tex
en_US -> en_GB + other minor stuff

@@
 %%% HRI 2015 -> double-blind review process
-
+%
 %\numberofauthors{1} 
@@
 We present an eye-tracking study on an educational robot
-Thymio II with 52 participants. The participants observed the robot
+Thymio II~\cite{riedo2012two} with 52 participants. The participants observed the robot
 detecting obstacles in the first phase of the experiment and they
@@
 gaze of the participants was recorded during both the phases. The values
-from the robot's sensors were visualized on the robot's body using LEDs
+from the robot's sensors were visualised on the robot's body using LEDs
 in two different ways in the two experimental conditions and there was
-no sensor data visualization in the control condition. We found that the
-sensor data visualization has an impact on the gaze patterns and the
+no sensor data visualisation in the control condition. We found that the
+sensor data visualisation has an impact on the gaze patterns and the
 performance of the participants. The main goal of the experiment was to
@@
 the researchers design better interactive scenarios in the future. These
-features include the conceptual mapping of the sensor data visualization and the
-robot's function and the generalizing the concepts to solve a given problem in a
+features include the conceptual mapping of the sensor data visualisation and the
+robot's function and the generalising the concepts to solve a given problem in a
 contextual learning environment. ~
@@
 attention through the LEDs. We can use this feature to guide the users'
-attention in a way that the effectiveness of the interaction is maximized. In
+attention in a way that the effectiveness of the interaction is maximised. In
 the case of interaction with the educational robots the effect of the
@@
 Our working hypothesis is that with careful mapping between the LED
-visualizations and the behavior of the robot we can induce the understanding of
+visualisations and the behaviour of the robot we can induce the understanding of
 the functionality of the robot very easily. We propose to use the gaze data to
 verify this hypothesis. With eye-tracking data we can judge whether the mapping
-between the behavior and visual actuators is useful or not for the participants'
-understanding.  Moreover, we hypothesize that the good performers will be able
+between the behaviour and visual actuators is useful or not for the participants'
+understanding.  Moreover, we hypothesise that the good performers will be able
 to anticipate the robot's motion. Eye-tracking data can also be useful to verify
@@
 reaching a certain target.  After each phase the participant explain the
-behavior of the robot. The sensor data was visualized through LEDs with three
-visualization conditions: {\sf TRUE} visualization, {\sf RANDOM} visualization and {\sf NONE}
-visualization. Through this experiment we investigate the following research
+behaviour of the robot. The sensor data was visualised through LEDs with three
+visualisation conditions: {\sf TRUE} visualisation, {\sf RANDOM} visualisation and {\sf NONE}
+visualisation. Through this experiment we investigate the following research
 questions:
@@
 
-The rest of the paper is organized as follows. The second section gives
+The rest of the paper is organised as follows. The second section gives
 a brief review of the eye-tracking research done to quantify the
@@
 task-based performance. In a pair-programming task, \cite{jermann2012effects}
-showed that the good performing pairs have more synchronized gaze on different
+showed that the good performing pairs have more synchronised gaze on different
 parts of a program than the bad performing pairs. In a similar task,
@@
 that previous research provides insights about the relationship between the gaze
-patterns and the behavioral and task-based performance indicators in diverse
+patterns and the behavioural and task-based performance indicators in diverse
 scenarios.
@@
 
-In the experiment, there were 3 sensor data visualization conditions.  For the
-{\sf TRUE} visualization condition, the number of illuminated LEDs, on the top of the
+In the experiment, there were 3 sensor data visualisation conditions.  For the
+{\sf TRUE} visualisation condition, the number of illuminated LEDs, on the top of the
 robot, is proportional to the intensity measured by the IR-sensor. When the
 intensity of the reflected IR crosses a predefined threshold, the robot does a
-90° turn to its right. For the two other conditions, the behavior is the same,
+90° turn to its right. For the two other conditions, the behaviour is the same,
 simply the display changes. In the {\sf RANDOM} condition, the display shows as if the
@@
 The playground (Figure~\ref{playground}) is designed in order to allow the
-participants to get a reference of the previous behavior of the robot, as well
-as to allow us to localize the position of the robot, the position of the
+participants to get a reference of the previous behaviour of the robot, as well
+as to allow us to localise the position of the robot, the position of the
 obstacles and the position of the gaze on the video recorded from the
-eye-tracker. The localization is made possible by the use of unique fiducial
+eye-tracker. The localisation is made possible by the use of unique fiducial
 markers on the playground. On the right hand side, the observation phase takes
@@
     \caption{\small Basic playground for the experiment. The fiducial markers
-    are used for automatic localization of the gaze pointers on the observation
+    are used for automatic localisation of the gaze pointers on the observation
     video.}
@@
 
-One important fact to be considered is that the localization of the
+One important fact to be considered is that the localisation of the
 robot, the obstacle or the gaze pointer on the observation field for the
@@
 approaching obstacles. The robot turns as soon as it detects the
-obstacle. The participant watches the robot's behavior for a black and a
+obstacle. The participant watches the robot's behaviour for a black and a
 white obstacle for 5 trials each. For the white, the robot turns
@@
 trial the robot is equipped with a pen to draw its trajectory for both
-obstacles with different colors. After drawing, the participant is asked
+obstacles with different colours. After drawing, the participant is asked
 the question: ``How does the robot work?''
@@
 \paragraph{Interaction phase} In the second phase, the participant is asked
-to guide the robot to a goal, using a gray obstacle. The participant can put the
+to guide the robot to a goal, using a grey obstacle. The participant can put the
 obstacle wherever he likes on the left hand side (Figure~\ref{playground}) of
-the playground before the robot starts. We designed the gray obstacle to reflect
+the playground before the robot starts. We designed the grey obstacle to reflect
 more infrared light (IR) than the black or the white obstacles therefore the
@@
     \caption{\small Experimental setup for observation phase. The observation
-    video is recorded from the video camer in the front of the eye tracker (in
+    video is recorded from the video camera in the front of the eye tracker (in
     the lop-left corner).}
@@
 or programming aspects of the robot, a high level represents describing
-the behavior. For the levels of correctness, we categorized the
+the behaviour. For the levels of correctness, we categorised the
 responses into correct or incorrect response. In TABLE I. we present
@@
         \midrule
-        \textit{incorrect} & \textit{low} & ``The robot turns at a given distance in respect to a color, defined in the program.''\\ 
+        \textit{incorrect} & \textit{low} & ``The robot turns at a given distance in respect to a colour, defined in the program.''\\ 
         \midrule
-        \textit{incorrect} & \textit{high} & `Gray is the most dangerous, so the
+        \textit{incorrect} & \textit{high} & `Grey is the most dangerous, so the
         robot turn really early.''\\ 
         \midrule
-        \textit{correct} & \textit{low} & ``The gray obstacle reflects a lot,
+        \textit{correct} & \textit{low} & ``The grey obstacle reflects a lot,
         the robot sends light. At a certain threshold the robot turns.'' \\ 
         \midrule
-        \textit{correct} & \textit{high} & ``The gray obstacle is shinier, so
+        \textit{correct} & \textit{high} & ``The grey obstacle is shinier, so
         more reflective, and better detectable.''\\ 
@@
 
-    \item The participant identified a wrong cause for the behavior of the robot:
+    \item The participant identified a wrong cause for the behaviour of the robot:
         ``The robot notices the tags on the side''.
@@
     \item The participant held the code responsible for the cause of different
-        behavior: ``The robot turns at a given distance in respect to a color,
+        behaviour: ``The robot turns at a given distance in respect to a color,
         defined in the program''.
@@
     \item The participant tried to explain by analogies or did not explain the
-        robots behavior at an understandable level: ``Gray is the most
+        robots behaviour at an understandable level: ``Grey is the most
         dangerous, so the robot turns really early''.
@@
 longer period of time. The various fixation detection algorithms are
-summarized in~\cite{duchowski2007eye}. Following are the two gaze measures, derived
+summarised in~\cite{duchowski2007eye}. Following are the two gaze measures, derived
 from the fixations, which we used in the present work.
@@
 by the robot in the observation phase is for the participants to be able
-to refer to the prior behavior of the robot in the interaction phase. We
+to refer to the prior behaviour of the robot in the interaction phase. We
 measured the amount of time a participant looks at the reference side
@@
 the final answer. Surprisingly there is no correlation between the
-visualization condition and the correctness or abstraction of the
+visualisation condition and the correctness or abstraction of the
 answers given. We could not find any anticipation patterns in the
@@
 the {\sf NONE} condition ($F[2,49]=3.68$, p = .03). This depicts that the
-sensor data visualization has an effect on the users' attention.
+sensor data visualisation has an effect on the users' attention.
 
@@
 
-The fact that the participants in the {\sf RANDOM} or {\sf NONE} visualization
+The fact that the participants in the {\sf RANDOM} or {\sf NONE} visualisation
 condition improved more than those with {\sf TRUE} condition is surprising
@@
 participants who see the robot in the {\sf TRUE} condition have a stronger
-believe that the robot always behaves the same. They see the LEDs of the
+belief that the robot always behaves the same. They see the LEDs of the
 robot turning on and therefore the robot still works. The ones with {\sf NONE}
-visualization do not have an indication whether the robot works the same
+visualisation do not have an indication whether the robot works the same
 way as in the observation phase, and start experimenting earlier. The
@@
 hypothesis that a carefully designed mapping between the robot's
-behavior and its visual actuators can help in maximizing the learning
+behavior and its visual actuators can help in maximising the learning
 effect during the interaction.
+
+Another plausible explanation for the participants in {\sf NONE} and {\sf RANDOM} condition
+being better performers than the {\sf TRUE} condition during the interaction phase
+comes from the transparency of the robot's behaviour. The robot's
+behaviour was not at all transparent in the former two conditions. This might
+have caused the participants to put more effort in understanding the behaviour.
+Therefore, they performed better.
 
@@
 The advantages of mobile eye-tracking come with an additional cost. As
-we mentioned earlier, the automatic localization of the gaze pointer on
+we mentioned earlier, the automatic localisation of the gaze pointer on
 the visual stimulus is not a trivial task. To do this we have to use a
@@
 fiducial markers.
-
-Another plausible explanation for the participants in {\sf NONE} and {\sf RANDOM} condition
-being better performers than the {\sf TRUE} condition during the interaction phase
-comes from the transparency of the robot's behavior. The robot's
-behavior was not at all transparent in the former two conditions. This might
-have caused the participants to put more effort in understanding the behavior.
-Therefore, they performed better.
 
@@
 We addressed two research questions in the beginning of the present
-work. The results show that the way the sensor data is visualized has an
+work. The results show that the way the sensor data is visualised has an
 impact on both the gaze patterns and the performance (Question 2).
@@
 said that there should be clear and carefully designed mapping between
-the robots' behavior and the sensor data visualization. Its environment
-also affects the behavior of the robot and hence the environment also
+the robots' behaviour and the sensor data visualization. Its environment
+also affects the behaviour of the robot and hence the environment also
 should be taken into consideration while designing the
-behavior-visualization mapping. We introduced a novelty (the gray
+behavior-visualisation mapping. We introduced a novelty (the gray
 obstacle being more reflective) in the environment during the
@@
 session for the participants, which can later be tested during the
-interaction phase. Any novel behavior modality (in our case, the more
-reflective gray obstacle) can have a negative impact on the
+interaction phase. Any novel behaviour modality (in our case, the more
+reflective grey obstacle) can have a negative impact on the
 participants' understanding.

### 2014-10-02 paper.tex
Reorganisation of the paper for HRI 'Enabling methods'

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Related Work: Gaze patterns and Expertise/Task based performance}
+\section{State of Eye Tracking in Human-Robot Interaction}
+
+\subsection{Eye Tracking as an Interaction Modality}
+
+\subsection{Eye Tracking as a tool to Measure Joint Attention}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Eye Tracking as a Tool for Assessing Social Interaction}
+
+\subsection{Gaze patterns and Expertise/Task based performance}
 
@@
 
-\section{Experiment}
+\section{Method Description}
+
+\subsection{Gaze measures}
+
+The most common form of eye-tracking data aggregation are the fixations.
+Fixations depict the periods in the user's observation when the user
+attends a relatively small part of the visual stimulus for a relatively
+longer period of time. The various fixation detection algorithms are
+summarised in~\cite{duchowski2007eye}. Following are the two gaze measures, derived
+from the fixations, which we used in the present work.
+
+Average fixation duration on the robot: We measured the amount of time a
+participant looks at the robot and averaged this duration for the number
+of fixations on the robot for the particular participant.
+
+Average fixation on the reference side: The main area (right hand side
+of figure 2) in the observation phase is treated as the reference side
+in the interaction phase. The rationale behind keeping the lines drawn
+by the robot in the observation phase is for the participants to be able
+to refer to the prior behaviour of the robot in the interaction phase. We
+measured the amount of time a participant looks at the reference side
+and averaged this duration for the number of fixations on the reference
+side for the particular participant.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Field of Application and Deployment}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Method Application}
 
@@
 
-\subsection{Gaze measures}
-
-The most common form of eye-tracking data aggregation are the fixations.
-Fixations depict the periods in the user's observation when the user
-attends a relatively small part of the visual stimulus for a relatively
-longer period of time. The various fixation detection algorithms are
-summarised in~\cite{duchowski2007eye}. Following are the two gaze measures, derived
-from the fixations, which we used in the present work.
-
-Average fixation duration on the robot: We measured the amount of time a
-participant looks at the robot and averaged this duration for the number
-of fixations on the robot for the particular participant.
-
-Average fixation on the reference side: The main area (right hand side
-of figure 2) in the observation phase is treated as the reference side
-in the interaction phase. The rationale behind keeping the lines drawn
-by the robot in the observation phase is for the participants to be able
-to refer to the prior behaviour of the robot in the interaction phase. We
-measured the amount of time a participant looks at the reference side
-and averaged this duration for the number of fixations on the reference
-side for the particular participant.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Results}
+\subsection{Results}
 
@@
 
-\subsection{Average fixation duration on the robot during observation phase
+\subsubsection{Average fixation duration on the robot during observation phase
 vs.~condition}
@@
 
-\subsection{First improvement vs.~condition}
+\subsubsection{First improvement vs.~condition}
 
@@
 
-\subsection{Average fixation duration on the reference side during interaction
+\subsubsection{Average fixation duration on the reference side during interaction
 phase vs.~condition}
@@
 
-\subsection{First improvement vs number of fixations on reference side}
+\subsubsection{First improvement vs number of fixations on reference side}
 

### 2014-10-02 paper.tex
Re-organisation of method description
Updated title and abstract

@@
 \title{\LARGE \bf
-    Eye tracking with Educational Robots: A Cautionary Tale
+    Eye-Tracking: a New Look at Human-Robot Interaction Assessment
 }
@@
 
-We present an eye-tracking study on an educational robot
-Thymio II~\cite{riedo2012two} with 52 participants. The participants observed the robot
-detecting obstacles in the first phase of the experiment and they
-interacted with the robot in the second phase of the experiment.
-Finally, they were asked to explain the functionality of the robot. The
-gaze of the participants was recorded during both the phases. The values
-from the robot's sensors were visualised on the robot's body using LEDs
-in two different ways in the two experimental conditions and there was
-no sensor data visualisation in the control condition. We found that the
-sensor data visualisation has an impact on the gaze patterns and the
-performance of the participants. The main goal of the experiment was to
-investigate that eye tracking could bring insights to the effectiveness
-of the interaction between the human user and the robot.
+Eye-tracking has been previously shown to be an effective proxy to understand
+complex socio-cognitive interactions. Yet its application to human-robot
+interactions (HRI) remains limited. This article presents the state of the
+art in eye-tracking methods for interaction assessment, and explores how those
+are applicable to HRI.
+
+Techniques based on mobile eye-tracking as well as the main analysis approaches
+for eye-tracking data are first exhaustively presented, with an emphasis on
+those we believe relevant to robotics. We then report on a study involving the
+educational robot Thymio II~\cite{riedo2012two} with 52 participants: the
+students have to explain a pre-programmed behaviour of the robot with or without
+the help of visual cues. The study setup and analysis illustrate how to apply
+eye-tracking techniques to actual human-robot interaction situations.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Eye-tracking}
 
-\section{Method Application}
+\subsubsection{Apparatus}
+\begin{enumerate}
+\item Stationary
+\item Mobile 
+\item Dual eye-tracking
+
+\end {enumerate}
+
+\subsubsection{Mobile Eye-tracking setup}
+
+\begin{enumerate}
+\item Calibration
+\item Recording Scene 
+\item Recording Gaze
+
+\end {enumerate}
+
+\subsubsection{Use cases for mobile eye-tracking}
+
+\begin{enumerate}
+\item Stationary target, stationary observer
+\item Moving target, stationary observer
+\item Stationary target, moving observer
+\item Moving target, moving observer
+\end{enumerate}
+
+\subsection{Data and Analysis}
+
+\begin{enumerate}
+\item Fixaitons
+\item Saccades and transitions
+\item Smooth Persuite
+\item Areas of Interest
+\item Heatmaps
+
+\end {enumerate}
+
+\subsection{Joint attention and social behaviour analysis}
+
+\section{Method Application Example}
 

### 2014-10-02 paper.tex
Re-organisation of results and discussion

@@
 
-We had two measures of performance. First measure was a rating given to
-the responses that participants gave to the question about the
-functionality of the robot. Second measure was the distance from the
-target in the interaction phase.
+%We had two measures of performance. First measure was a rating given to
+%the responses that participants gave to the question about the
+%functionality of the robot. Second measure was the distance from the
+%target in the interaction phase.
 
-We transcribed the responses to perform a rating scheme on the level of
-abstraction and correctness. A low level of abstraction consists in
-describing the functionality of the robot in the terms of the electric
-or programming aspects of the robot, a high level represents describing
-the behaviour. For the levels of correctness, we categorised the
-responses into correct or incorrect response. In TABLE I. we present
-sample responses for the different categories.
+%We transcribed the responses to perform a rating scheme on the level of
+%abstraction and correctness. A low level of abstraction consists in
+%describing the functionality of the robot in the terms of the electric
+%or programming aspects of the robot, a high level represents describing
+%the behaviour. For the levels of correctness, we categorised the
+%responses into correct or incorrect response. In TABLE I. we present
+%sample responses for the different categories.
 
-\begin{table}[ht!]
-    \centering
-    \footnotesize
-    \begin{tabular}{ccp{4.5cm}}
-        \toprule
-        Correct. & Abstract. & Sample answer \\
-        \midrule
-        \textit{incorrect} & \textit{low} & ``The robot turns at a given distance in respect to a colour, defined in the program.''\\ 
-        \midrule
-        \textit{incorrect} & \textit{high} & `Grey is the most dangerous, so the
-        robot turn really early.''\\ 
-        \midrule
-        \textit{correct} & \textit{low} & ``The grey obstacle reflects a lot,
-        the robot sends light. At a certain threshold the robot turns.'' \\ 
-        \midrule
-        \textit{correct} & \textit{high} & ``The grey obstacle is shinier, so
-        more reflective, and better detectable.''\\ 
-        \bottomrule
-    \end{tabular}
-    \caption{Sample answers for all classes}
+%\begin{table}[ht!]
+%    \centering
+%    \footnotesize
+%    \begin{tabular}{ccp{4.5cm}}
+%        \toprule
+%        Correct. & Abstract. & Sample answer \\
+%        \midrule
+%        \textit{incorrect} & \textit{low} & ``The robot turns at a given distance in respect to a colour, defined in the program.''\\ 
+%        \midrule
+%        \textit{incorrect} & \textit{high} & `Grey is the most dangerous, so the
+%        robot turn really early.''\\ 
+%        \midrule
+%        \textit{correct} & \textit{low} & ``The grey obstacle reflects a lot,
+%        the robot sends light. At a certain threshold the robot turns.'' \\ 
+%        \midrule
+%        \textit{correct} & \textit{high} & ``The grey obstacle is shinier, so
+%        more reflective, and better detectable.''\\ 
+%        \bottomrule
+%    \end{tabular}
+%    \caption{Sample answers for all classes}
+%
+%    \label{sample_answer}
+%\end{table}
 
-    \label{sample_answer}
-\end{table}
-
-Second, the distances from the target were measured for all 5 trials. As
+We measured the distances from the target were measured for all 5 trials. As
 a matter of fact, as soon as the principle of the robot was deemed to be
@@
 
-Incorrect answers were further classified into 4 categories; we present
-each category accompanied by a sample response:
-
-\begin{itemize}
-    \item The participant did not respond or offer a possible explanation: ``I
-        really don't know how the robot works''.
-
-    \item The participant identified a wrong cause for the behaviour of the robot:
-        ``The robot notices the tags on the side''.
-
-    \item The participant held the code responsible for the cause of different
-        behaviour: ``The robot turns at a given distance in respect to a color,
-        defined in the program''.
-
-    \item The participant tried to explain by analogies or did not explain the
-        robots behaviour at an understandable level: ``Grey is the most
-        dangerous, so the robot turns really early''.
-
-\end{itemize}
+%Incorrect answers were further classified into 4 categories; we present
+%each category accompanied by a sample response:
+%
+%\begin{itemize}
+%    \item The participant did not respond or offer a possible explanation: ``I
+%        really don't know how the robot works''.
+%
+%    \item The participant identified a wrong cause for the behaviour of the robot:
+%        ``The robot notices the tags on the side''.
+%
+%    \item The participant held the code responsible for the cause of different
+%        behaviour: ``The robot turns at a given distance in respect to a color,
+%        defined in the program''.
+%
+%    \item The participant tried to explain by analogies or did not explain the
+%        robots behaviour at an understandable level: ``Grey is the most
+%        dangerous, so the robot turns really early''.
+%
+%\end{itemize}
 
@@
 
-\section{Discussion}
+\section{Interpreting the results}
 
-We present an eye-tracking study in the context of human-robot
-interaction with an educational setting. The fact that participants have
-higher average fixation duration on the robot during the observation
-phase in the {\sf NONE} condition than the other two conditions (Figure 4) is
-not surprising as displaying visual information on the robot induces a
-saliency effect on the attention and the gaze is attracted towards the
-salient feature in the field of view.
+We present an exemplar eye-tracking study in the context of human-robot
+interaction within an educational setting.
+In this section we give an example of "how to interpret the eye-tracking results".
+The fact that participants have higher average fixation duration on the robot during the observation phase in the {\sf NONE} condition than the other two conditions (Figure 4) is not surprising as displaying visual information on the robot induces a saliency effect on the attention and the gaze is attracted towards the salient feature in the field of view.
+
+The fact that the participants in the {\sf RANDOM} or {\sf NONE} visualisation condition improved more than those with {\sf TRUE} condition is surprising (Figure 5).
+There are two plausible explanations.
+The first is that participants who see the robot in the {\sf TRUE} condition have a stronger belief that the robot always behaves the same.
+They see the LEDs of the robot turning on and therefore the robot still works.
+The ones with {\sf NONE} visualisation do not have an indication whether the robot works the same way as in the observation phase, and start experimenting earlier.
+The second explanation is that the participants in {\sf TRUE} condition just put the obstacles out of detection range, because they could see different display information and concluded therefore it may behave differently.
 
@@
 hypothesis that a carefully designed mapping between the robot's
-behavior and its visual actuators can help in maximising the learning
+behaviour and its visual actuators can help in maximising the learning
 effect during the interaction.
 
-Another plausible explanation for the participants in {\sf NONE} and {\sf RANDOM} condition
-being better performers than the {\sf TRUE} condition during the interaction phase
-comes from the transparency of the robot's behaviour. The robot's
-behaviour was not at all transparent in the former two conditions. This might
-have caused the participants to put more effort in understanding the behaviour.
-Therefore, they performed better.
+%Another plausible explanation for the participants in {\sf NONE} and {\sf RANDOM} condition
+%being better performers than the {\sf TRUE} condition during the interaction phase
+%comes from the transparency of the robot's behaviour. The robot's
+%behaviour was not at all transparent in the former two conditions. This might
+%have caused the participants to put more effort in understanding the behaviour.
+%Therefore, they performed better.
+\section{Discussion}
 
@@
 
-We addressed two research questions in the beginning of the present
-work. The results show that the way the sensor data is visualised has an
-impact on both the gaze patterns and the performance (Question 2).
-However, for the relation between the gaze patterns of the participants
-and their performance outcomes (Question 1) we cannot claim a direct
-relation. We found a negative correlation between the gaze-patterns and
-the first improvement during the interaction phase. We could not find a
-relation between the explanation of the participants and their
-gaze-patterns. Moreover, we did not find any anticipation patterns in
-the gaze data. The lack of evidence for the relation between
-participants' explanations and their gaze patterns prevents us to make
-any strong claims about the relation between the overall performance and
-the gaze patterns.
-
-The fact that we cannot find a relation between the gaze patterns and
-all the factors in the performance might have its roots in the way we
-designed the interaction phase experiment. As a working hypothesis we
-said that there should be clear and carefully designed mapping between
-the robots' behaviour and the sensor data visualization. Its environment
-also affects the behaviour of the robot and hence the environment also
-should be taken into consideration while designing the
-behavior-visualisation mapping. We introduced a novelty (the gray
-obstacle being more reflective) in the environment during the
-interaction phase of the experiment that forced the participants to
-revise their hypothesis and hence they failed to understand the robot's
-functionality. This also serves as a word of caution in future while
-designing such interactions. The observation phase serves as a training
-session for the participants, which can later be tested during the
-interaction phase. Any novel behaviour modality (in our case, the more
-reflective grey obstacle) can have a negative impact on the
-participants' understanding.
+%We addressed two research questions in the beginning of the present
+%work. The results show that the way the sensor data is visualised has an
+%impact on both the gaze patterns and the performance (Question 2).
+%However, for the relation between the gaze patterns of the participants
+%and their performance outcomes (Question 1) we cannot claim a direct
+%relation. We found a negative correlation between the gaze-patterns and
+%the first improvement during the interaction phase. We could not find a
+%relation between the explanation of the participants and their
+%gaze-patterns. Moreover, we did not find any anticipation patterns in
+%the gaze data. The lack of evidence for the relation between
+%participants' explanations and their gaze patterns prevents us to make
+%any strong claims about the relation between the overall performance and
+%the gaze patterns.
+%
+%The fact that we cannot find a relation between the gaze patterns and
+%all the factors in the performance might have its roots in the way we
+%designed the interaction phase experiment. As a working hypothesis we
+%said that there should be clear and carefully designed mapping between
+%the robots' behaviour and the sensor data visualization. Its environment
+%also affects the behaviour of the robot and hence the environment also
+%should be taken into consideration while designing the
+%behavior-visualisation mapping. We introduced a novelty (the gray
+%obstacle being more reflective) in the environment during the
+%interaction phase of the experiment that forced the participants to
+%revise their hypothesis and hence they failed to understand the robot's
+%functionality. This also serves as a word of caution in future while
+%designing such interactions. The observation phase serves as a training
+%session for the participants, which can later be tested during the
+%interaction phase. Any novel behaviour modality (in our case, the more
+%reflective grey obstacle) can have a negative impact on the
+%participants' understanding.
 

### 2014-10-02 paper.tex
Conclusion modified

@@
 %Therefore, they performed better.
-\section{Discussion}
+\section{Conclusion}
 
@@
 variables to assess not only the task-based performance of the
-participants but also to evaluate HRI. The prime advantage of using
+participants but also to analyse HRI situations. The prime advantage of using
 mobile eye-tracking is that the users' interaction with the robot can
@@
 
-Another advantage of using mobile eye-tracking to evaluate HRI,
-especially in an educational context, is that the data provides direct
-and noise free access to the users' attention. While in other
-physiological measures for attention, such as EEG, the data has a lot of
-noise and the relation to the attention is very task-specific.
+Another advantage of using mobile eye-tracking to assess HRI situations, is that the data provides direct and noise free access to the users' attention.
+While in other physiological measures for attention, such as EEG, the data has a lot of noise and the relation to the attention is very task-specific.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
 

### 2014-10-02 paper.tex
Experiment from introduction removed

@@
 
-Our working hypothesis is that with careful mapping between the LED
-visualisations and the behaviour of the robot we can induce the understanding of
-the functionality of the robot very easily. We propose to use the gaze data to
-verify this hypothesis. With eye-tracking data we can judge whether the mapping
-between the behaviour and visual actuators is useful or not for the participants'
-understanding.  Moreover, we hypothesise that the good performers will be able
-to anticipate the robot's motion. Eye-tracking data can also be useful to verify
-the anticipation hypothesis.
-
-The experiment consists in two phases. The first phase is the observation phase
-during which the participants watch the robot move and detect an obstacle in a
-``playground''. The second phase requires the participants to interact with the
-robot by placing an obstacle in its path to make it detect the obstacle before
-reaching a certain target.  After each phase the participant explain the
-behaviour of the robot. The sensor data was visualised through LEDs with three
-visualisation conditions: {\sf TRUE} visualisation, {\sf RANDOM} visualisation and {\sf NONE}
-visualisation. Through this experiment we investigate the following research
-questions:
-
-\begin{enumerate}
-    \item Are there different gaze patterns for different levels of performance
-during the interaction? Moreover, can we see any anticipation patterns
-for the good performers?
-
-    \item How does displaying the sensor information on the robot' body as a
-visual cue affects the gaze and performance of the participants?
-\end{enumerate}
-
-The rest of the paper is organised as follows. The second section gives
-a brief review of the eye-tracking research done to quantify the
-expertise and performance. The third section presents the specificities
-of the study. The fourth section lists the main results. The fifth
-section discusses the results. Finally, the sixth section concludes the
-paper.
+%Our working hypothesis is that with careful mapping between the LED
+%visualisations and the behaviour of the robot we can induce the understanding of
+%the functionality of the robot very easily. We propose to use the gaze data to
+%verify this hypothesis. With eye-tracking data we can judge whether the mapping
+%between the behaviour and visual actuators is useful or not for the participants'
+%understanding.  Moreover, we hypothesise that the good performers will be able
+%to anticipate the robot's motion. Eye-tracking data can also be useful to verify
+%the anticipation hypothesis.
+%
+%The experiment consists in two phases. The first phase is the observation phase
+%during which the participants watch the robot move and detect an obstacle in a
+%``playground''. The second phase requires the participants to interact with the
+%robot by placing an obstacle in its path to make it detect the obstacle before
+%reaching a certain target.  After each phase the participant explain the
+%behaviour of the robot. The sensor data was visualised through LEDs with three
+%visualisation conditions: {\sf TRUE} visualisation, {\sf RANDOM} visualisation and {\sf NONE}
+%visualisation. Through this experiment we investigate the following research
+%questions:
+%
+%\begin{enumerate}
+%    \item Are there different gaze patterns for different levels of performance
+%during the interaction? Moreover, can we see any anticipation patterns
+%for the good performers?
+%
+%    \item How does displaying the sensor information on the robot' body as a
+%visual cue affects the gaze and performance of the participants?
+%\end{enumerate}
+%
+%The rest of the paper is organised as follows. The second section gives
+%a brief review of the eye-tracking research done to quantify the
+%expertise and performance. The third section presents the specificities
+%of the study. The fourth section lists the main results. The fifth
+%section discusses the results. Finally, the sixth section concludes the
+%paper.
 

### 2014-10-02 paper.tex
Updated state of the art sections
Moved EEG/fMRI to intro

@@
 Eye tracking provides unprecedented access to the users' attention and
-engagement during interactive scenarios. Previous research has shown
+engagement during interactive scenarios. Previous research\fixme{refs} has shown
 that gaze data can be used as a proxy to understand the underlying
@@
 robot's function and the generalising the concepts to solve a given problem in a
-contextual learning environment. ~
+contextual learning environment.
 
@@
 
-We present a study with combining eye tracking and human robot interaction (HRI)
-in an educational setting. ~Eye tracking data is of high temporal precision as
+We propose to use the mobile eye trackers to be able to have our participants
+freely move on the experiment site. Using mobile eye tracker poses a technical
+challenge to automatically locate where the participants are looking. This is
+not a trivial task as the visual stimulus for participants is changing with
+every bit of motion of their head. This is the reason we used fiducial-markers
+on the maze we used in the experiment so that we can reconstruct the whole maze
+even if only a part of it is the visual field of the participant.
+
+\paragraph{Biometric Measurements of Interaction}
+
+\fixme{organize/rewrite this paragraph}
+
+\fixme{Mention skin conductance as well}
+
+Evaluation of HRI is mostly done through qualitative questionnaires and
+qualitative data (interaction videos, interviews for example). The physiological
+measurements such as eye tracking being precise, pertinent and portable at the
+same time provides an added value to the researcher.  However, this needs to be
+complemented with the qualitative data as well.
+
+Eye-tracking data is of high temporal precision as
 compared to some of the physiological data sources such as fMRI or other
@@
 
-Evaluation of HRI is mostly done through qualitative questionnaires and
-qualitative data (interaction videos, interviews for example). The physiological
-measurements such as eye tracking being precise, pertinent and portable at the
-same time provides an added value to the researcher.  However, this needs to be
-complemented with the qualitative data as well.
+The prime advantage of using mobile eye-tracking is that the users' interaction
+with the robot can still be ecologically valid. On the other hand, using fMRI
+for evaluating HRI reduces the interaction to a video of the robot only
+~\cite{rosenthal2013neural}.
 
-We propose to use the mobile eye trackers to be able to have our participants
-freely move on the experiment site. Using mobile eye tracker poses a technical
-challenge to automatically locate where the participants are looking. This is
-not a trivial task as the visual stimulus for participants is changing with
-every bit of motion of their head. This is the reason we used fiducial-markers
-on the maze we used in the experiment so that we can reconstruct the whole maze
-even if only a part of it is the visual field of the participant.
+Another advantage of using mobile eye-tracking to assess HRI situations, is that
+the data provides direct and noise free access to the users' attention. While in
+other physiological measures for attention, such as EEG, the data has a lot of
+noise and the relation to the attention is very task-specific.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{State of Eye Tracking in Human-Robot Interaction}
-
-\subsection{Eye Tracking as an Interaction Modality}
-
-\subsection{Eye Tracking as a tool to Measure Joint Attention}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Eye Tracking as a Tool for Assessing Social Interaction}
@@
 
+\subsection{Gaze patterns and Collaborative work}
+
 Our previous work also show a clear relation between gaze patterns and
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{State of Eye Tracking in Human-Robot Interaction}
+
+\subsection{Eye Tracking as an Interaction Modality}
+
+Controlling robot with gaze
+
+\subsection{Eye Tracking as a tool to Measure Joint Attention}
+
 It must be noted that to our best knowledge only very few studies have
@@
 was consistent irrespectively of the ambiguity of the situation. 
+SAY ABOUT THE VIDEO BASED INTERACTION
 
@@
 
-\section{Method Description}
-
-\subsection{Gaze measures}
-
-The most common form of eye-tracking data aggregation are the fixations.
-Fixations depict the periods in the user's observation when the user
-attends a relatively small part of the visual stimulus for a relatively
-longer period of time. The various fixation detection algorithms are
-summarised in~\cite{duchowski2007eye}. Following are the two gaze measures, derived
-from the fixations, which we used in the present work.
-
-Average fixation duration on the robot: We measured the amount of time a
-participant looks at the robot and averaged this duration for the number
-of fixations on the robot for the particular participant.
-
-Average fixation on the reference side: The main area (right hand side
-of figure 2) in the observation phase is treated as the reference side
-in the interaction phase. The rationale behind keeping the lines drawn
-by the robot in the observation phase is for the participants to be able
-to refer to the prior behaviour of the robot in the interaction phase. We
-measured the amount of time a participant looks at the reference side
-and averaged this duration for the number of fixations on the reference
-side for the particular participant.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Field of Application and Deployment}
+\section{Method description}
 
@@
 \begin{enumerate}
-\item Fixaitons
+\item Fixations: The most common form of eye-tracking data aggregation are the fixations.
+Fixations depict the periods in the user's observation when the user
+attends a relatively small part of the visual stimulus for a relatively
+longer period of time. The various fixation detection algorithms are
+summarised in~\cite{duchowski2007eye}.
+
 \item Saccades and transitions
-\item Smooth Persuite
+\item Smooth Pursuit
 \item Areas of Interest
-\item Heatmaps
+\item Heat-maps
 
@@
 {\sf TRUE}, there were 18, 17 and 17 participants respectively.
+
+\subsection{Eye-tracking measures}
+
+Average fixation duration on the robot: We measured the amount of time a
+participant looks at the robot and averaged this duration for the number
+of fixations on the robot for the particular participant.
+
+Average fixation on the reference side: The main area (right hand side
+of figure 2) in the observation phase is treated as the reference side
+in the interaction phase. The rationale behind keeping the lines drawn
+by the robot in the observation phase is for the participants to be able
+to refer to the prior behaviour of the robot in the interaction phase. We
+measured the amount of time a participant looks at the reference side
+and averaged this duration for the number of fixations on the reference
+side for the particular participant.
 
@@
 %Therefore, they performed better.
+
 \section{Conclusion}
@@
 variables to assess not only the task-based performance of the
-participants but also to analyse HRI situations. The prime advantage of using
-mobile eye-tracking is that the users' interaction with the robot can
-still be ecologically valid. On the other hand, using fMRI for
-evaluating HRI reduces the interaction to a video of the robot only
-~\cite{rosenthal2013neural}.
-
-Another advantage of using mobile eye-tracking to assess HRI situations, is that the data provides direct and noise free access to the users' attention.
-While in other physiological measures for attention, such as EEG, the data has a lot of noise and the relation to the attention is very task-specific.
+participants but also to analyse HRI situations.
 

### 2014-10-02 paper.tex
updated eye-tracking literature for HRI

@@
 \cite{sharif2012eye} showed that the expert programmers scan through all the
-lines in the program faster than the novices. In a collaborative Tetris game,
+lines in the program faster than the novices. In a Tetris game,
 \cite{jermann2010using} showed that experts pay more attention to the stack of
@@
 
-\subsection{Gaze patterns and Collaborative work}
+\subsection{Gaze patterns and Collaborative performance}
 
-Our previous work also show a clear relation between gaze patterns and
-task-based performance. In a pair-programming task, \cite{jermann2012effects}
+Previous work also show a clear relation between gaze patterns and
+task-based performance in collaborative settings. 
+CITE RICK DALE
+
+In a pair-programming task, \cite{jermann2012effects}
 showed that the good performing pairs have more synchronised gaze on different
@@
 
+The literature on the
+
 \subsection{Eye Tracking as an Interaction Modality}
@@
 
-\subsection{Eye Tracking as a tool to Measure Joint Attention}
+\subsection{Eye Tracking as a tool to Assess Interaction Algorithms}
+
+Physiological and subjective evaluation of a human?robot object hand-over task
+
+\subsection{Eye Tracking as a tool to Assess Joint Attention}
 
@@
 was consistent irrespectively of the ambiguity of the situation.
-SAY ABOUT THE VIDEO BASED INTERACTION
 

### 2014-10-02 paper.tex
Added HRI and eye-tracking refs

@@
 task-based performance in collaborative settings.
-CITE RICK DALE
-
-In a pair-programming task, \cite{jermann2012effects}
-showed that the good performing pairs have more synchronised gaze on different
-parts of a program than the bad performing pairs. In a similar task,
-\cite{sharma2012gaze} showed that the good performing pairs pay more attention
-to the data-flow of the program than the poor performing pairs. Moreover,
-\cite{sharma2013understanding} showed that while describing the functionality of
-a program the well performing teams had more gaze on the variable modification
-parts in the program while poor performing teams have equal distribution of gaze
-on different parts of the program during similar phase of the task.  Thus we see
-that previous research provides insights about the relationship between the gaze
-patterns and the behavioural and task-based performance indicators in diverse
-scenarios.
+As a measure of joint attention in collaborative settings  \cite{richardson2007art} proposed gaze recurrence between the collaborators and showed it to be correlated with the collaboration quality of the pair.
+In a pair-programming task, \cite{jermann2012effects} showed that the good performing pairs have more synchronised gaze on different parts of a program than the bad performing pairs.
+In a similar task, \cite{sharma2012gaze} showed that the good performing pairs pay more attention to the data-flow of the program than the poor performing pairs.
+Moreover, \cite{sharma2013understanding} showed that while describing the functionality of a program the well performing teams had more gaze on the variable modification parts in the program while poor performing teams have equal distribution of gaze on different parts of the program during similar phase of the task.
+Thus we see that previous research provides insights about the relationship between the gaze patterns and the behavioural and task-based performance indicators in diverse scenarios.
 
@@
 
-Controlling robot with gaze
+Controlling robot with gaze \cite{bhuiyan2004tracking}
 
@@
 
-Physiological and subjective evaluation of a human?robot object hand-over task
+Physiological and subjective evaluation of a human-robot object hand-over task  \cite{dehais2011physiological}
 

### 2014-10-02 paper.tex
complete State of Eye Tracking in HRI

@@
 
-The literature on the
+The usage of eye-tracking methods in HRI is very sparse.
+It must be noted that to our best knowledge only very few attempts to use eye-tracking as an interaction modality or as an interaction assessment technique in HRI.
 
@@
 
-Controlling robot with gaze \cite{bhuiyan2004tracking}
+To guide the motion of a robot \cite{bhuiyan2004tracking} used real time  gaze data of a human user.
+The users were able to provide the visual and geometrical motion information to the robot by moving their eyes in different parts of the human-robot interface.
 
@@
 
-Physiological and subjective evaluation of a human-robot object hand-over task  \cite{dehais2011physiological}
+To evaluate the effectiveness of the motion planning algorithm for a robot \cite{dehais2011physiological} used eye-tracking techniques.
+In an object hand-over task between a robot and a human, the authors compared various motion planning algorithms based on the gaze of the human.
 
@@
 
-It must be noted that to our best knowledge only very few studies have
-investigated how eye-tracking could be used to assess HRI. In an eye-tracking
-study, in the context of human robot interaction, \cite{staudte2009visual} found
+ In an eye-tracking study, in the context of human robot interaction, \cite{staudte2009visual} found
 that when the robot provides a matching visual and verbal reference to an object
@@
 was consistent irrespectively of the ambiguity of the situation.
+The video based interaction modality was used by the authors.
+This constraints the  interaction of the human-robot dyad to just a video.
+However, the stimulus (video) for eye-tracking provides strong contrast and a good control for experimental conditions.
 

### 2014-10-02 paper.tex
Added missing fixme package
update abstract

@@
 \newcommand{\ie}{{\textit{i.e.~}}}
+
+\usepackage[draft,footnote,nomargin]{fixme}
 
@@
 Eye tracking provides unprecedented access to the users' attention and
-engagement during interactive scenarios. Previous research\fixme{refs} has shown
+engagement during interactive scenarios. Previous research \cite{hasse2012measure,tien2010measuring,jermann2010using,sharma2012gaze} has shown
 that gaze data can be used as a proxy to understand the underlying

### 2014-10-02 paper.tex
[wip] conclusion

@@
 
-We demonstrated that eye-tracking data can provide several process
-variables to assess not only the task-based performance of the
-participants but also to analyse HRI situations.
+The task that we have presented was initially motivated by those two questions:
 
-The advantages of mobile eye-tracking come with an additional cost. As
+\begin{enumerate}
+    \item Can we characterise the participants' behaviours that
+        lead to good performance during the interaction? In particular, do
+        we observe any anticipation patterns for the good performers?
+
+    \item How does visual cue affects the performance of the participants?
+
+\end{enumerate}
+
+The task was performance-oriented and yet we were interested in accessing and
+understanding the cognitive mechanisms at stake during the interaction: where do
+the participant look when they want to understand a robot behaviour? does
+\emph{anticipation} reflect understanding? how the robot's design impact the
+interaction?
+
+We believe that mobile eye-tracking, as a relatively non-invasive yet accurate
+(both spatially and temporally) biometric measurement, is a key tool to
+investigate this kind of questions in ecologically valid environments.
+
+One need to be aware of its limitations: eye-tracking does not give a direct
+access to underlying mental representations, and a gaze pattern does not
+automatically tell us what the subject think of (EEG or fMRI may be slightly
+closer to that target, but they come with their own range of limitations).
+
+Besides, mobile eye-tracking come with an additional cost. As
 we mentioned earlier, the automatic localisation of the gaze pointer on
-the visual stimulus is not a trivial task. To do this we have to use a
-number of fiducial markers to the playground (Figure 2). We observed
-that the fiducial markers cause a distraction to the participants. As a
-future work, we are trying to find a suitable replacement to the
-fiducial markers.
+the visual stimulus is not a trivial task. In our study, we relied on a 
+number of fiducial markers to the playground, but they were reported as
+distractive by the participants. More complex computer vision tools (object
+tracking) can alleviate the need for such markers, but it certainly requires
+significant pre-processing prior to data analysis.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The results show that the way the sensor data is visualised has an
+impact on both the gaze patterns and the performance (Question 2).
+However, for the relation between the gaze patterns of the participants
+and their performance outcomes (Question 1) we cannot claim a direct
+relation. We found a negative correlation between the gaze-patterns and
+the first improvement during the interaction phase. We could not find a
+relation between the explanation of the participants and their
+gaze-patterns. Moreover, we did not find any anticipation patterns in
+the gaze data. The lack of evidence for the relation between
+participants' explanations and their gaze patterns prevents us to make
+any strong claims about the relation between the overall performance and
+the gaze patterns.
 
-Our effort to use the confluent of eye tracking and human-robot
-interaction provides insights to two aspects: first, as a way to
-evaluate the human-robot interaction and second, as a way to evaluate
-the interaction scenario.
-
-%We addressed two research questions in the beginning of the present
-%work. The results show that the way the sensor data is visualised has an
-%impact on both the gaze patterns and the performance (Question 2).
-%However, for the relation between the gaze patterns of the participants
-%and their performance outcomes (Question 1) we cannot claim a direct
-%relation. We found a negative correlation between the gaze-patterns and
-%the first improvement during the interaction phase. We could not find a
-%relation between the explanation of the participants and their
-%gaze-patterns. Moreover, we did not find any anticipation patterns in
-%the gaze data. The lack of evidence for the relation between
-%participants' explanations and their gaze patterns prevents us to make
-%any strong claims about the relation between the overall performance and
-%the gaze patterns.
 %

### 2014-10-02 paper.tex
Updated method application example

@@
 \section{Method Application Example}
+In this section, we present a mobile eye-tracking study with an educational robot Thymio II.
+The study exemplifies one of the use cases of the mobile eye-tracking.
+One part of the target (the robot) was moving, whereas the rest of the maze (or playground, figure~\ref{playground}, as we refer to it in the rest of this paper) was stationary.
+The participants were allowed to move but most of them remained seated for the duration of the experiment.
+For the purpose of the eye-tracking data analysis, we used the proportions of fixations on different  area of interest on the playground.
 

### 2014-10-02 paper.tex
updated procedure
fixed the introduction- no fix me

@@
 
-\fixme{organize/rewrite this paragraph}
-
-\fixme{Mention skin conductance as well}
-
 Evaluation of HRI is mostly done through qualitative questionnaires and
@@
 measurements such as eye tracking being precise, pertinent and portable at the
-same time provides an added value to the researcher.  However, this needs to be
-complemented with the qualitative data as well.
-
-Eye-tracking data is of high temporal precision as
-compared to some of the physiological data sources such as fMRI or other
+same time provides an added value to the researcher.  Eye-tracking data is of high temporal precision as compared to some of the physiological data sources such as fMRI or other
 biometric devices used to measure the palpitation and the body temperature. The
@@
 access to the users' attention than other portable and physiological data
-sources such as EEG; this makes eye-tracking data a pertinent source to measure
+sources such as EEG and wristbands measuring skin conductance and pulse rate; this makes eye-tracking data a pertinent source to measure
 attention.
@@
 \subsubsection{Apparatus}
+
+\fixme{tell about the spatial and temporal resolution of different eye-trackers}
+
 \begin{enumerate}
@@
 as expertise). The participants were placed in front of the playground
-(Figure~\ref{expe}) and were equipped with the SMI eye-tracking glasses. The
+(Figure~\ref{expe}) and were equipped with the SMI eye-tracking glasses.
+The eye-tracker records the gaze data at 30Hz with an accuracy of 0.5 degrees at 40 centimetres distance; and the scene camera of the eye-tracking glasses records the video in HD.
+The
 actual experiment consisted in two phases: observation phase and

### 2014-10-02 paper.tex
Work on the conclusion

@@
 understanding the cognitive mechanisms at stake during the interaction: where do
-the participant look when they want to understand a robot behaviour? does
-\emph{anticipation} reflect understanding? how the robot's design impact the
+the participant look when they want to understand a robot behaviour? Does
+\emph{anticipation} reflect understanding? How the robot's design impact the
 interaction?
@@
 
-One need to be aware of its limitations: eye-tracking does not give a direct
+In that regard, we identify three main strengths of eye-tracking. First,
+eye-tracking introduce less experimental bias: mobile eye-tracker are
+non-invasive and lightweight. Combined with mobile recording units, they do not
+put any constraints on participant movements, contrary to traditional techniques
+like video recording. Also, contrary to questionnaires or interview-based
+protocol where the experimenter active role may influence the assessment,
+eye-tracker are easy to ``forget about'' for the participants.
+
+Second, eye-tracking provides a direct, un-mediated access to the subject's
+attentional focus~\cite{sharma2014withmeness} (both spatially -- where does the
+subject look at -- and temporally -- where does the subject's attention stays).
+Importantly, this information leads to a fine-grained measure of
+\emph{engagement}.  Also, the good temporal resolution of eye-trackers allows
+for the accurate study of the \emph{dynamics} of attention: what are the
+attentional patterns of the subject during the interaction.
+
+Third, it has been showed in literature that eye-tracking can provide an
+effective measure of higher socio-cognitive behaviours: it can be used as a
+predictor for successful joint task achievement~\cite{sharma2013understanding},
+or as a measure of \emph{interaction quality}~\cite{jermann2012effects} through
+measurement of joint attention.
+
+One need however to be aware of its limitations: eye-tracking does not give a direct
 access to underlying mental representations, and a gaze pattern does not
@@
 
-The results show that the way the sensor data is visualised has an
-impact on both the gaze patterns and the performance (Question 2).
-However, for the relation between the gaze patterns of the participants
-and their performance outcomes (Question 1) we cannot claim a direct
-relation. We found a negative correlation between the gaze-patterns and
-the first improvement during the interaction phase. We could not find a
-relation between the explanation of the participants and their
-gaze-patterns. Moreover, we did not find any anticipation patterns in
-the gaze data. The lack of evidence for the relation between
-participants' explanations and their gaze patterns prevents us to make
-any strong claims about the relation between the overall performance and
-the gaze patterns.
+Still, we believe that eye-tracking, as a method for the assessment and
+understanding of the complex cognitive mechanisms that underlie human-robot
+interaction, is a promising tool, currently under-used in robotics.
 
-%
-%The fact that we cannot find a relation between the gaze patterns and
-%all the factors in the performance might have its roots in the way we
-%designed the interaction phase experiment. As a working hypothesis we
-%said that there should be clear and carefully designed mapping between
-%the robots' behaviour and the sensor data visualization. Its environment
-%also affects the behaviour of the robot and hence the environment also
-%should be taken into consideration while designing the
-%behavior-visualisation mapping. We introduced a novelty (the gray
-%obstacle being more reflective) in the environment during the
-%interaction phase of the experiment that forced the participants to
-%revise their hypothesis and hence they failed to understand the robot's
-%functionality. This also serves as a word of caution in future while
-%designing such interactions. The observation phase serves as a training
-%session for the participants, which can later be tested during the
-%interaction phase. Any novel behaviour modality (in our case, the more
-%reflective grey obstacle) can have a negative impact on the
-%participants' understanding.
-
-In a nutshell, the use of gaze data as an assessment of the human-robot
-interaction in an educational setting provides future research
-prospects. The data acquisition is a better trade-off between the
-ecological validity of the experiment (as there cannot be an interaction
-with the robot fMRI data acquisition) and the precision of the data
-stream (wristbands for measuring the palpitation and the temperature).
+%In a nutshell, the use of gaze data as an assessment of the human-robot
+%interaction in an educational setting provides future research
+%prospects. The data acquisition is a better trade-off between the
+%ecological validity of the experiment (as there cannot be an interaction
+%with the robot fMRI data acquisition) and the precision of the data
+%stream (wristbands for measuring the palpitation and the temperature).
 

### 2014-10-02 paper.tex
Moved paragraph on wristband to biometric tools

@@
 
-\paragraph{Biometric Measurements of Interaction}
-
-Evaluation of HRI is mostly done through qualitative questionnaires and
-qualitative data (interaction videos, interviews for example). The physiological
-measurements such as eye tracking being precise, pertinent and portable at the
-same time provides an added value to the researcher.  Eye-tracking data is of high temporal precision as compared to some of the physiological data sources such as fMRI or other
-biometric devices used to measure the palpitation and the body temperature. The
-eye tracking devices are portable enough as opposed to the bulky apparatus used
-in fMRI~\cite{rosenthal2013neural}.  Eye tracking data provides more direct
-access to the users' attention than other portable and physiological data
-sources such as EEG and wristbands measuring skin conductance and pulse rate; this makes eye-tracking data a pertinent source to measure
-attention.
-
-The prime advantage of using mobile eye-tracking is that the users' interaction
-with the robot can still be ecologically valid. On the other hand, using fMRI
-for evaluating HRI reduces the interaction to a video of the robot only
-~\cite{rosenthal2013neural}.
-
-Another advantage of using mobile eye-tracking to assess HRI situations, is that
-the data provides direct and noise free access to the users' attention. While in
-other physiological measures for attention, such as EEG, the data has a lot of
-noise and the relation to the attention is very task-specific.
-
 %Our working hypothesis is that with careful mapping between the LED
@@
 %paper.
+
+\paragraph{Biometric Measurements of Interaction}
+
+Evaluation of HRI is mostly done through qualitative questionnaires and
+qualitative data (interaction videos, interviews for example). The physiological
+measurements such as eye tracking being precise, pertinent and portable at the
+same time provides an added value to the researcher.  Eye-tracking data is of high temporal precision as compared to some of the physiological data sources such as fMRI or other
+biometric devices used to measure the palpitation and the body temperature. The
+eye tracking devices are portable enough as opposed to the bulky apparatus used
+in fMRI~\cite{rosenthal2013neural}.  Eye tracking data provides more direct
+access to the users' attention than other portable and physiological data
+sources such as EEG and wristbands measuring skin conductance and pulse rate; this makes eye-tracking data a pertinent source to measure
+attention.
+
+The prime advantage of using mobile eye-tracking is that the users' interaction
+with the robot can still be ecologically valid. On the other hand, using fMRI
+for evaluating HRI reduces the interaction to a video of the robot only
+~\cite{rosenthal2013neural}.
+
+Another advantage of using mobile eye-tracking to assess HRI situations, is that
+the data provides direct and noise free access to the users' attention. While in
+other physiological measures for attention, such as EEG, the data has a lot of
+noise and the relation to the attention is very task-specific.
+
+In a nutshell, the use of gaze data as an assessment of the human-robot
+interaction in an educational setting provides future research
+prospects. The data acquisition is a better trade-off between the
+ecological validity of the experiment (as there cannot be an interaction
+with the robot fMRI data acquisition) and the precision of the data
+stream (wristbands for measuring the palpitation and the temperature).
 
@@
 
-%In a nutshell, the use of gaze data as an assessment of the human-robot
-%interaction in an educational setting provides future research
-%prospects. The data acquisition is a better trade-off between the
-%ecological validity of the experiment (as there cannot be an interaction
-%with the robot fMRI data acquisition) and the precision of the data
-%stream (wristbands for measuring the palpitation and the temperature).
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-10-02 paper.tex
update bibtex

@@
 access to the users' attention than other portable and physiological data
-sources such as EEG and wristbands measuring skin conductance and pulse rate; this makes eye-tracking data a pertinent source to measure
-attention.
+sources such as EEG and wristbands measuring skin conductance and pulse rate; this makes eye-tracking data a pertinent source to measure attention.
 
@@
 
-\subsection{Joint attention and social behaviour analysis}
+\subsection{Analysing social behaviour}
+
+\begin{enumerate}
+\item Joint attention
+\item interaction episodes
+\end{enumerate}
 
@@
 The task was performance-oriented and yet we were interested in accessing and
-understanding the cognitive mechanisms at stake during the interaction: where do
-the participant look when they want to understand a robot behaviour? Does
+understanding the cognitive mechanisms at stake during the interaction: where do participants look when they want to understand a robot behaviour? Does
 \emph{anticipation} reflect understanding? How the robot's design impact the

### 2014-10-02 paper.tex
last version at 2:10:14:15:00

@@
 
-On the other hand, educational robots can be of great use in making young school
-kids interested in technological developments~\cite{cooper1999robots,
-wyffels2010building}. It is important to know about the key socio-cognitive
-features of this subset of human-robot interaction because these features let
-the researchers design better interactive scenarios in the future. These
-features include the conceptual mapping of the sensor data visualisation and the
-robot's function and the generalising the concepts to solve a given problem in a
-contextual learning environment.
-
-Thymio II~\cite{riedo2012two} can provide salient effects onto our visual
-attention through the LEDs. We can use this feature to guide the users'
-attention in a way that the effectiveness of the interaction is maximised. In
-the case of interaction with the educational robots the effect of the
-interaction is to make the users understand the technical aspects of the robot
-and to make the users be able to transfer it to different domains.
-
-We propose to use the mobile eye trackers to be able to have our participants
-freely move on the experiment site. Using mobile eye tracker poses a technical
-challenge to automatically locate where the participants are looking. This is
-not a trivial task as the visual stimulus for participants is changing with
-every bit of motion of their head. This is the reason we used fiducial-markers
-on the maze we used in the experiment so that we can reconstruct the whole maze
-even if only a part of it is the visual field of the participant.
+%On the other hand, educational robots can be of great use in making young school
+%kids interested in technological developments~\cite{cooper1999robots,
+%wyffels2010building}. It is important to know about the key socio-cognitive
+%features of this subset of human-robot interaction because these features let
+%the researchers design better interactive scenarios in the future. These
+%features include the conceptual mapping of the sensor data visualisation and the
+%robot's function and the generalising the concepts to solve a given problem in a
+%contextual learning environment.
+%
+%Thymio II~\cite{riedo2012two} can provide salient effects onto our visual
+%attention through the LEDs. We can use this feature to guide the users'
+%attention in a way that the effectiveness of the interaction is maximised. In
+%the case of interaction with the educational robots the effect of the
+%interaction is to make the users understand the technical aspects of the robot
+%and to make the users be able to transfer it to different domains.
 
@@
 stream (wristbands for measuring the palpitation and the temperature).
+
+\paragraph{Article overview}
+\fixme{write it}
 
@@
 For the purpose of the eye-tracking data analysis, we used the proportions of fixations on different  area of interest on the playground.
+
+We propose to use the mobile eye trackers to be able to have our participants
+freely move on the experiment site. Using mobile eye tracker poses a technical
+challenge to automatically locate where the participants are looking. This is
+not a trivial task as the visual stimulus for participants is changing with
+every bit of motion of their head. This is the reason we used fiducial-markers
+on the maze we used in the experiment so that we can reconstruct the whole maze
+even if only a part of it is the visual field of the participant.
 

### 2014-10-02 paper.tex
Article overview

@@
 measurements such as eye tracking being precise, pertinent and portable at the
-same time provides an added value to the researcher.  Eye-tracking data is of high temporal precision as compared to some of the physiological data sources such as fMRI or other
-biometric devices used to measure the palpitation and the body temperature. The
-eye tracking devices are portable enough as opposed to the bulky apparatus used
-in fMRI~\cite{rosenthal2013neural}.  Eye tracking data provides more direct
-access to the users' attention than other portable and physiological data
-sources such as EEG and wristbands measuring skin conductance and pulse rate; this makes eye-tracking data a pertinent source to measure attention.
+same time provides an added value to the researcher.  Eye-tracking data is of
+high temporal precision as compared to some of the physiological data sources
+such as fMRI or other biometric devices used to measure the palpitation and the
+body temperature. The eye tracking devices are portable enough as opposed to the
+bulky apparatus used in fMRI~\cite{rosenthal2013neural}. Eye tracking data
+provides more direct access to the users' attention than other portable and
+physiological data sources such as EEG and wristbands measuring skin conductance
+and pulse rate; this makes eye-tracking data a pertinent source to measure
+attention.
 
@@
 with the robot can still be ecologically valid. On the other hand, using fMRI
-for evaluating HRI reduces the interaction to a video of the robot only
-~\cite{rosenthal2013neural}.
+for evaluating HRI reduces the interaction to a video of the robot
+only~\cite{rosenthal2013neural}.
 
@@
 In a nutshell, the use of gaze data as an assessment of the human-robot
-interaction in an educational setting provides future research
-prospects. The data acquisition is a better trade-off between the
-ecological validity of the experiment (as there cannot be an interaction
-with the robot fMRI data acquisition) and the precision of the data
-stream (wristbands for measuring the palpitation and the temperature).
+interaction in an educational setting provides future research prospects. The
+data acquisition is a better trade-off between the ecological validity of the
+experiment (as there cannot be an interaction with the robot fMRI data
+acquisition) and the precision of the data stream (wristbands for measuring the
+palpitation and the temperature).
 
 \paragraph{Article overview}
-\fixme{write it}
+
+The article is structured as follow: section~\ref{et_assessing} presents the
+main lines of research in eye-tracking-based assessment of cognitive
+tasks and interaction. It evidences the breadth of the field, both on individual
+and social tasks. Section~\ref{et_robotics} contrasts this literature with the
+current state-of-the-art of eye-tracking in HRI. We distinguish here two main
+applications: eye-tracking as an \emph{interaction modality} and eye-tracking as
+an \emph{interaction assessment} tool. It appears that the literature in both
+these fields is scarce.
+
+Section~\ref{method} presents in a brief yet exhaustive way eye-tracking as an
+investigation method: we introduce the main eye-tracking techniques (including
+mobile eye-tracking and dual eye-tracking) and discuss their respective domains
+of application. We then present five important techniques for eye-tracking data
+analysis and emphasise the analysis techniques that are the most relevant to the
+study of social interaction.
+
+Next, section~\ref{application} presents a case study with 52 subjects
+interacting with a robot. The study acts both as a demonstration of the
+integration of eye-tracking in HRI studies, and as an example of a possible
+eye-tracking setup. Then, section~\ref{interpretation} goes over the analysis of
+the study data and its interpretation, and illustrates this process.
+
+We conclude the article with a summary of the strengths of eye-tracking to
+analyse the complex socio-cognitive situations that characterise human-robot
+interaction, as well as a few notes on the limitations of this method.
 
@@
 \section{Eye Tracking as a Tool for Assessing Social Interaction}
+\label{et_assessing}
 
@@
 \section{State of Eye Tracking in Human-Robot Interaction}
+\label{et_robotics}
 
@@
 \section{Method description}
+\label{method}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Eye-tracking}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Method Application Example}
+\label{application}
+
 In this section, we present a mobile eye-tracking study with an educational robot Thymio II.
@@
 \section{Interpreting the results}
+\label{interpretation}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusion}
+\label{conclusion}
 

### 2014-10-02 paper.tex
Put both 'results' and 'interpretation' in the same section
[formatting] line wrapping

@@
 Eye tracking provides unprecedented access to the users' attention and
-engagement during interactive scenarios. Previous research \cite{hasse2012measure,tien2010measuring,jermann2010using,sharma2012gaze} has shown
-that gaze data can be used as a proxy to understand the underlying
+engagement during interactive scenarios. Previous research
+\cite{hasse2012measure,tien2010measuring,jermann2010using,sharma2012gaze} has
+shown that gaze data can be used as a proxy to understand the underlying
 socio-cognitive aspects in not only human-computer interaction but in
 human-human interaction as well. In the present decade, off the shelf
-eye-trackers have become readily available to the researchers to assess
-the users' attention and engagement.
+eye-trackers have become readily available to the researchers to assess the
+users' attention and engagement.
 
@@
 
-Previous work also show a clear relation between gaze patterns and
-task-based performance in collaborative settings.
-As a measure of joint attention in collaborative settings  \cite{richardson2007art} proposed gaze recurrence between the collaborators and showed it to be correlated with the collaboration quality of the pair.
-In a pair-programming task, \cite{jermann2012effects} showed that the good performing pairs have more synchronised gaze on different parts of a program than the bad performing pairs.
-In a similar task, \cite{sharma2012gaze} showed that the good performing pairs pay more attention to the data-flow of the program than the poor performing pairs.
-Moreover, \cite{sharma2013understanding} showed that while describing the functionality of a program the well performing teams had more gaze on the variable modification parts in the program while poor performing teams have equal distribution of gaze on different parts of the program during similar phase of the task.
-Thus we see that previous research provides insights about the relationship between the gaze patterns and the behavioural and task-based performance indicators in diverse scenarios.
+Previous work also show a clear relation between gaze patterns and task-based
+performance in collaborative settings. As a measure of joint attention in
+collaborative settings  \cite{richardson2007art} proposed gaze recurrence
+between the collaborators and showed it to be correlated with the collaboration
+quality of the pair. In a pair-programming task, \cite{jermann2012effects}
+showed that the good performing pairs have more synchronised gaze on different
+parts of a program than the bad performing pairs. In a similar task,
+\cite{sharma2012gaze} showed that the good performing pairs pay more attention
+to the data-flow of the program than the poor performing pairs. Moreover,
+\cite{sharma2013understanding} showed that while describing the functionality of
+a program the well performing teams had more gaze on the variable modification
+parts in the program while poor performing teams have equal distribution of gaze
+on different parts of the program during similar phase of the task.  Thus we see
+that previous research provides insights about the relationship between the gaze
+patterns and the behavioural and task-based performance indicators in diverse
+scenarios.
 
@@
 
-The usage of eye-tracking methods in HRI is very sparse.
-It must be noted that to our best knowledge only very few attempts to use eye-tracking as an interaction modality or as an interaction assessment technique in HRI.
+The usage of eye-tracking methods in HRI is very sparse. It must be noted that
+to our best knowledge only very few attempts to use eye-tracking as an
+interaction modality or as an interaction assessment technique in HRI.
 
@@
 
-To guide the motion of a robot \cite{bhuiyan2004tracking} used real time  gaze data of a human user.
-The users were able to provide the visual and geometrical motion information to the robot by moving their eyes in different parts of the human-robot interface.
+To guide the motion of a robot \cite{bhuiyan2004tracking} used real time  gaze
+data of a human user. The users were able to provide the visual and geometrical
+motion information to the robot by moving their eyes in different parts of the
+human-robot interface.
 
@@
 
-To evaluate the effectiveness of the motion planning algorithm for a robot \cite{dehais2011physiological} used eye-tracking techniques.
-In an object hand-over task between a robot and a human, the authors compared various motion planning algorithms based on the gaze of the human.
+To evaluate the effectiveness of the motion planning algorithm for a robot
+\cite{dehais2011physiological} used eye-tracking techniques. In an object
+hand-over task between a robot and a human, the authors compared various motion
+planning algorithms based on the gaze of the human.
 
@@
 
- In an eye-tracking study, in the context of human robot interaction, \cite{staudte2009visual} found
-that when the robot provides a matching visual and verbal reference to an object
-the participants were more likely to look at the correct objects. This result
-was consistent irrespectively of the ambiguity of the situation.
-The video based interaction modality was used by the authors.
+In an eye-tracking study, in the context of human robot interaction,
+\cite{staudte2009visual} found that when the robot provides a matching visual
+and verbal reference to an object the participants were more likely to look at
+the correct objects. This result was consistent irrespectively of the ambiguity
+of the situation. The video based interaction modality was used by the authors.
 This constraints the  interaction of the human-robot dyad to just a video.
-However, the stimulus (video) for eye-tracking provides strong contrast and a good control for experimental conditions.
+However, the stimulus (video) for eye-tracking provides strong contrast and a
+good control for experimental conditions.
 
@@
 
-In this section, we present a mobile eye-tracking study with an educational robot Thymio II.
-The study exemplifies one of the use cases of the mobile eye-tracking.
-One part of the target (the robot) was moving, whereas the rest of the maze (or playground, figure~\ref{playground}, as we refer to it in the rest of this paper) was stationary.
-The participants were allowed to move but most of them remained seated for the duration of the experiment.
-For the purpose of the eye-tracking data analysis, we used the proportions of fixations on different  area of interest on the playground.
+In this section, we present a mobile eye-tracking study with an educational
+robot Thymio II. The study exemplifies one of the use cases of the mobile
+eye-tracking. One part of the target (the robot) was moving, whereas the rest of
+the maze (or playground, figure~\ref{playground}, as we refer to it in the rest
+of this paper) was stationary. The participants were allowed to move but most of
+them remained seated for the duration of the experiment. For the purpose of the
+eye-tracking data analysis, we used the proportions of fixations on different
+area of interest on the playground.
 
@@
 
-Upon their arrival at the experiment site, the participants signed a
-consent form and answered a small questionnaire about demographics and
-participant's experience with educational robots (this we later consider
-as expertise). The participants were placed in front of the playground
-(Figure~\ref{expe}) and were equipped with the SMI eye-tracking glasses.
-The eye-tracker records the gaze data at 30Hz with an accuracy of 0.5 degrees at 40 centimetres distance; and the scene camera of the eye-tracking glasses records the video in HD.
-The
-actual experiment consisted in two phases: observation phase and
-interaction phase.
+Upon their arrival at the experiment site, the participants signed a consent
+form and answered a small questionnaire about demographics and participant's
+experience with educational robots (this we later consider as expertise). The
+participants were placed in front of the playground (Figure~\ref{expe}) and were
+equipped with the SMI eye-tracking glasses. The eye-tracker records the gaze
+data at 30Hz with an accuracy of 0.5 degrees at 40 centimetres distance; and the
+scene camera of the eye-tracking glasses records the video in HD.  The actual
+experiment consisted in two phases: observation phase and interaction phase.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Interpreting the Results}
+\label{interpretation}
 
@@
 
-\section{Interpreting the results}
-\label{interpretation}
+\subsection{Interpretation}
 
 We present an exemplar eye-tracking study in the context of human-robot
-interaction within an educational setting.
-In this section we give an example of "how to interpret the eye-tracking results".
-The fact that participants have higher average fixation duration on the robot during the observation phase in the {\sf NONE} condition than the other two conditions (Figure 4) is not surprising as displaying visual information on the robot induces a saliency effect on the attention and the gaze is attracted towards the salient feature in the field of view.
+interaction within an educational setting. In this section we give an example of
+"how to interpret the eye-tracking results". The fact that participants have
+higher average fixation duration on the robot during the observation phase in
+the {\sf NONE} condition than the other two conditions (Figure 4) is not
+surprising as displaying visual information on the robot induces a saliency
+effect on the attention and the gaze is attracted towards the salient feature in
+the field of view.
 
-The fact that the participants in the {\sf RANDOM} or {\sf NONE} visualisation condition improved more than those with {\sf TRUE} condition is surprising (Figure 5).
-There are two plausible explanations.
-The first is that participants who see the robot in the {\sf TRUE} condition have a stronger belief that the robot always behaves the same.
-They see the LEDs of the robot turning on and therefore the robot still works.
-The ones with {\sf NONE} visualisation do not have an indication whether the robot works the same way as in the observation phase, and start experimenting earlier.
-The second explanation is that the participants in {\sf TRUE} condition just put the obstacles out of detection range, because they could see different display information and concluded therefore it may behave differently.
+The fact that the participants in the {\sf RANDOM} or {\sf NONE} visualisation
+condition improved more than those with {\sf TRUE} condition is surprising
+(Figure 5). There are two plausible explanations. The first is that participants
+who see the robot in the {\sf TRUE} condition have a stronger belief that the
+robot always behaves the same. They see the LEDs of the robot turning on and
+therefore the robot still works. The ones with {\sf NONE} visualisation do not
+have an indication whether the robot works the same way as in the observation
+phase, and start experimenting earlier. The second explanation is that the
+participants in {\sf TRUE} condition just put the obstacles out of detection
+range, because they could see different display information and concluded
+therefore it may behave differently.
 
@@
 The task was performance-oriented and yet we were interested in accessing and
-understanding the cognitive mechanisms at stake during the interaction: where do participants look when they want to understand a robot behaviour? Does
+understanding the cognitive mechanisms at stake during the interaction: where do
+participants look when they want to understand a robot behaviour? Does
 \emph{anticipation} reflect understanding? How the robot's design impact the

### 2014-10-02 paper.tex
Updated eye-tracking apparatus

@@
 users' attention and engagement.
-
-%On the other hand, educational robots can be of great use in making young school
-%kids interested in technological developments~\cite{cooper1999robots,
-%wyffels2010building}. It is important to know about the key socio-cognitive
-%features of this subset of human-robot interaction because these features let
-%the researchers design better interactive scenarios in the future. These
-%features include the conceptual mapping of the sensor data visualisation and the
-%robot's function and the generalising the concepts to solve a given problem in a
-%contextual learning environment.
-%
-%Thymio II~\cite{riedo2012two} can provide salient effects onto our visual
-%attention through the LEDs. We can use this feature to guide the users'
-%attention in a way that the effectiveness of the interaction is maximised. In
-%the case of interaction with the educational robots the effect of the
-%interaction is to make the users understand the technical aspects of the robot
-%and to make the users be able to transfer it to different domains.
-
-%Our working hypothesis is that with careful mapping between the LED
-%visualisations and the behaviour of the robot we can induce the understanding of
-%the functionality of the robot very easily. We propose to use the gaze data to
-%verify this hypothesis. With eye-tracking data we can judge whether the mapping
-%between the behaviour and visual actuators is useful or not for the participants'
-%understanding.  Moreover, we hypothesise that the good performers will be able
-%to anticipate the robot's motion. Eye-tracking data can also be useful to verify
-%the anticipation hypothesis.
-%
-%The experiment consists in two phases. The first phase is the observation phase
-%during which the participants watch the robot move and detect an obstacle in a
-%``playground''. The second phase requires the participants to interact with the
-%robot by placing an obstacle in its path to make it detect the obstacle before
-%reaching a certain target.  After each phase the participant explain the
-%behaviour of the robot. The sensor data was visualised through LEDs with three
-%visualisation conditions: {\sf TRUE} visualisation, {\sf RANDOM} visualisation and {\sf NONE}
-%visualisation. Through this experiment we investigate the following research
-%questions:
-%
-%\begin{enumerate}
-%    \item Are there different gaze patterns for different levels of performance
-%during the interaction? Moreover, can we see any anticipation patterns
-%for the good performers?
-%
-%    \item How does displaying the sensor information on the robot' body as a
-%visual cue affects the gaze and performance of the participants?
-%\end{enumerate}
-%
-%The rest of the paper is organised as follows. The second section gives
-%a brief review of the eye-tracking research done to quantify the
-%expertise and performance. The third section presents the specificities
-%of the study. The fourth section lists the main results. The fifth
-%section discusses the results. Finally, the sixth section concludes the
-%paper.
 
@@
 \subsection{Eye-tracking}
+First, we introduce the basic eye-tracking setups, technical steps in mobile eye-tracking and different use cases of mobile eye-tracking.
 
@@
 
-\fixme{tell about the spatial and temporal resolution of different eye-trackers}
+Most eye trackers work by projecting infrared light on the pupil and measuring the reflection with one or more cameras. . Following are the typical setups for the eye-trackers used in research:
 
 \begin{enumerate}
-\item Stationary
-\item Mobile 
-\item Dual eye-tracking
+\item Stationary: The stationary eye-trackers are widely used for the controlled laboratory experiments.
+These eye-trackers have a separate eye-tracking device (camera, infrared source and microprocessor) and a monitor or a monitor embedded with different parts  of the eye-tracking devices.
+The data rate is usually higher than the mobile eye-trackers (ranging between 60 Hz to 2000 Hz).
+The accuracy of current devices is about 0.5 degrees, which correspond to 0.35 mm for a user whose head is placed at 40 cm from the screen.
+The setup needs the heads of the participants to be fixed using a opthalmologic head rest for better data quality.
+
+\item Mobile: Mobile eye-trackers are useful to conduct more ecologically valid and naturalistic experiments.
+These eye-trackers have a scene camera in the front to record the visual field of the participants.
+Present mobile eye-trackers have a data rate of 30 Hz and a spatial accuracy equal to the stationary eye-trackers.
+
+\item Dual eye-tracking: Dual eye-tracking requires synchronisation of two eye-trackers, so that the researchers can record the gaze data for a pair of collaborators without any lag (as the clocks of two systems can not be perfectly synchronised).
+\cite{nussli2011dual} explored and compared different ways to synchronise two eye-trackers.
 
@@
 \item Fixations: The most common form of eye-tracking data aggregation are the fixations.
-Fixations depict the periods in the user's observation when the user
-attends a relatively small part of the visual stimulus for a relatively
-longer period of time. The various fixation detection algorithms are
-summarised in~\cite{duchowski2007eye}.
+Fixations depict the periods in the user's observation when the user attends a relatively small part of the visual stimulus for a relatively longer period of time.
+The various fixation detection algorithms are summarised in~\cite{duchowski2007eye}.
 
-\item Saccades and transitions
+\item Saccades and transitions: Two fixations are connected by a saccade. Saccades are the sudden variations in the eye-movements. While analysing saccades, there are two 
 \item Smooth Pursuit
@@
 
-%We had two measures of performance. First measure was a rating given to
-%the responses that participants gave to the question about the
-%functionality of the robot. Second measure was the distance from the
-%target in the interaction phase.
-
-%We transcribed the responses to perform a rating scheme on the level of
-%abstraction and correctness. A low level of abstraction consists in
-%describing the functionality of the robot in the terms of the electric
-%or programming aspects of the robot, a high level represents describing
-%the behaviour. For the levels of correctness, we categorised the
-%responses into correct or incorrect response. In TABLE I. we present
-%sample responses for the different categories.
-
-%\begin{table}[ht!]
-%    \centering
-%    \footnotesize
-%    \begin{tabular}{ccp{4.5cm}}
-%        \toprule
-%        Correct. & Abstract. & Sample answer \\
-%        \midrule
-%        \textit{incorrect} & \textit{low} & ``The robot turns at a given distance in respect to a colour, defined in the program.''\\ 
-%        \midrule
-%        \textit{incorrect} & \textit{high} & `Grey is the most dangerous, so the
-%        robot turn really early.''\\ 
-%        \midrule
-%        \textit{correct} & \textit{low} & ``The grey obstacle reflects a lot,
-%        the robot sends light. At a certain threshold the robot turns.'' \\ 
-%        \midrule
-%        \textit{correct} & \textit{high} & ``The grey obstacle is shinier, so
-%        more reflective, and better detectable.''\\ 
-%        \bottomrule
-%    \end{tabular}
-%    \caption{Sample answers for all classes}
-%
-%    \label{sample_answer}
-%\end{table}
-
 We measured the distances from the target were measured for all 5 trials. As
@@
 improvement in the following sections.
-
-%Incorrect answers were further classified into 4 categories; we present
-%each category accompanied by a sample response:
-%
-%\begin{itemize}
-%    \item The participant did not respond or offer a possible explanation: ``I
-%        really don't know how the robot works''.
-%
-%    \item The participant identified a wrong cause for the behaviour of the robot:
-%        ``The robot notices the tags on the side''.
-%
-%    \item The participant held the code responsible for the cause of different
-%        behaviour: ``The robot turns at a given distance in respect to a color,
-%        defined in the program''.
-%
-%    \item The participant tried to explain by analogies or did not explain the
-%        robots behaviour at an understandable level: ``Grey is the most
-%        dangerous, so the robot turns really early''.
-%
-%\end{itemize}
 
@@
 
-%Another plausible explanation for the participants in {\sf NONE} and {\sf RANDOM} condition
-%being better performers than the {\sf TRUE} condition during the interaction phase
-%comes from the transparency of the robot's behaviour. The robot's
-%behaviour was not at all transparent in the former two conditions. This might
-%have caused the participants to put more effort in understanding the behaviour.
-%Therefore, they performed better.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-10-03 paper.tex
updated sections 4.2 and 4.3

@@
 
+Mobile eye-tracking requires more caution during data collection, as the heads and the bodies (in some cases) of the participants are free to move. We list the main challenges here:
+
 \begin{enumerate}
-\item Calibration
-\item Recording Scene 
-\item Recording Gaze
+\item Calibration: The calibration step of the mobile eye-trackers is crucial, as the head of the participant is always moving. The experimenter needs to make sure that while calibrating 
+\item Recording Scene and gaze: The mobile eye-trackers record the scene video and the gaze pointer information is given in the coordinate system of this video.
+\item Localisation of gaze pointer:  Using mobile eye tracker poses a technical challenge to automatically locate where the participants are actually looking.
+This is not a trivial task as the visual stimulus for participants is changing with every bit of motion of their head.
 
 \end {enumerate}
+
+\subsection{Data and Analysis}
+
+\begin{enumerate}
+\item Fixations: The most common form of eye-tracking data aggregation are the fixations.
+Fixations depict the periods in the user's observation when the user attends a relatively small part of the visual stimulus for a relatively longer period of time.
+The various fixation detection algorithms are summarised in~\cite{duchowski2007eye}.
+
+\item Saccades and transitions: Two fixations are connected by a saccade.
+Saccades are the sudden variations in the eye-movements.
+There are two main ways to analyse saccades: 1) saccade lengths are indicative of the amount of change in the attention; and 2) the two ends of a saccade denote a transition between two areas of scene/screen.
+
+\item Smooth Pursuit: This is a special type of event that gives insights about continuously following a moving object in the field of view.
+These events are analysed for their durations, especially when there is a moving target that the participants need to observe.
+
+\item Areas of Interest (AOI):   
+\item Heat-maps:
+
+\end {enumerate}
+
+\subsection{Analysing social behaviour}
+
+\begin{enumerate}
+
+\item Joint attention: Maintaining common grounds among the collaborators is key to success during collaborators.
+This is achieved via references to the objects visible by both the participants in a pair.
+There are two events that create a moment of joint attention: 1) eye-voice span \cite{griffin2000eyes}: the referencing partner looks at the referred site before referring to it; and 2) voice-eye span \cite{allopenna1998tracking}: after the reference the non- referencing partner looks at the referred site.
+These moments of joint attention help them to create the common ground in the first place and further, they help in maintaining the common ground.
+The time lag between the speaker's gaze and listener's gaze at the referred object is called gaze cross recurrence \cite{richardson2007art}.
+The gaze cross recurrence has been shown to be correlated with the collaboration quality and joint task performance \cite{nussli2011dual}.
+
+\item Interaction episodes: Apart from moments of joint attention, collaboration contains sequence of actions and communicative moves.
+To build a model of the interaction quality, it is essential to put temporal markers in the flow of interaction.
+\cite{sharma2012gaze} defined the segments of interaction by detecting stable (looking at a small set of objects) and together (looking at the same set of objects) moments.
+Simply put,
+for automatic assessment of quality of interaction, we need to find out how to automatically segment the interaction based on gaze data.
+It is important to keep in mind that different level of gaze aggregation can help in finding evidences for different granularities of task decomposition.
+\end{enumerate}
 
@@
 \item Moving target, moving observer
-\end{enumerate}
-
-\subsection{Data and Analysis}
-
-\begin{enumerate}
-\item Fixations: The most common form of eye-tracking data aggregation are the fixations.
-Fixations depict the periods in the user's observation when the user attends a relatively small part of the visual stimulus for a relatively longer period of time.
-The various fixation detection algorithms are summarised in~\cite{duchowski2007eye}.
-
-\item Saccades and transitions: Two fixations are connected by a saccade. Saccades are the sudden variations in the eye-movements. While analysing saccades, there are two 
-\item Smooth Pursuit
-\item Areas of Interest
-\item Heat-maps
-
-\end {enumerate}
-
-\subsection{Analysing social behaviour}
-
-\begin{enumerate}
-\item Joint attention
-\item interaction episodes
 \end{enumerate}
@@
 We propose to use the mobile eye trackers to be able to have our participants
-freely move on the experiment site. Using mobile eye tracker poses a technical
-challenge to automatically locate where the participants are looking. This is
-not a trivial task as the visual stimulus for participants is changing with
-every bit of motion of their head. This is the reason we used fiducial-markers
+freely move on the experiment site.This is the reason we used fiducial-markers
 on the maze we used in the experiment so that we can reconstruct the whole maze

### 2014-10-03 paper.tex
Updated section 4.2

@@
 
-\item Areas of Interest (AOI):   
+\item Areas of Interest (AOI):  AOIs are those parts of the scene/screen that the experimenter wants to analyse the interaction (with the interface or with another user / robot).
+These AOIs are usually based on the hypotheses of the experiment.
+For example, if in a usability study of a phone advertisement \footnote{http://eyetracking.com.ua/eng/visualization/12.html} (Figure \ref{aoi}) the screen can divided into the model, the object and the caption.
+Once the screen has been divided into AOIs, we can compare the gaze distribution for different users and /or different experimental conditions.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\linewidth]{nokia.jpg}
+    \caption{Example of dividing a screen in Areas of interest.
+    source: http://eyetracking.com.ua/eng/visualization/12.html}
+    \label{aoi}
+\end{figure}
+
 \item Heat-maps:
@@
 \subsection{Analysing social behaviour}
+
+Dual eye-tracking is more complicated to analyse than the solo eye-tracking, for the sole reason of the social dimension being involved in the users' behaviour.
+Following are the two main points to keep in mind while analysing the social behaviour of a collaborating pair of users:
 

### 2014-10-03 paper.tex
updated section 4.2 and figures

@@
 These AOIs are usually based on the hypotheses of the experiment.
-For example, if in a usability study of a phone advertisement \footnote{http://eyetracking.com.ua/eng/visualization/12.html} (Figure \ref{aoi}) the screen can divided into the model, the object and the caption.
+For example, if in a usability study of a phone advertisement \footnote{http://eyetracking.com.ua/eng/visualization/12.html} (Figure \ref{aoi}) the screen can divided into the advertisement model, the object and the caption.
 Once the screen has been divided into AOIs, we can compare the gaze distribution for different users and /or different experimental conditions.
@@
 
-\item Heat-maps:
+\item Heat maps: Heat maps are classical data visualisation tools.
+In terms of visualising eye-tracking data the heat maps show the distribution of the gaze.
+The distribution of the gaze then can be analysed for different user classes (for usability studies), experimental conditions or task based performance (Figures \ref{heatMapGood} and \ref {heatMapBad} \cite{sharma2014how}).
+The mathematical details about how to create the heat maps can be found in \cite{duchowski2007eye}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\linewidth]{heat-map-good-ex}
+    \caption{Example heat map for a MOOC student who performed well in the posttest.
+    source: \cite{sharma2014how}}
+    \label{heatMapGood}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\linewidth]{heat-map-bad-ex}
+    \caption{Example heat map for a MOOC student who performed poor in the posttest.
+    source: source: \cite{sharma2014how}}
+    \label{heatMapBad}
+\end{figure}
 
@@
 
+There are several use cases of mobile eye-tracking, we categorise them in following three categories:
+
 \begin{enumerate}
-\item Stationary target, stationary observer
 \item Moving target, stationary observer
@@
 \end{enumerate}
+
+Next, we present an example of one of the use cases of mobile eye-tracking.
 

### 2014-10-03 paper.tex
Merged the two heat map figs + AIO picture smaller
Full paper version 1
This is the first time when we have a complete draft of the paper, this
might be the final one as well (with a few changes here and there)

@@
     \centering
-    \includegraphics[width=0.9\linewidth]{nokia.jpg}
-    \caption{Example of dividing a screen in Areas of interest.
-    source: http://eyetracking.com.ua/eng/visualization/12.html}
+    \includegraphics[width=0.4\linewidth]{nokia.jpg}
+    \caption{Example of dividing a screen in Areas of interest. Source: http://eyetracking.com.ua/eng/visualization/12.html}
     \label{aoi}
@@
 In terms of visualising eye-tracking data the heat maps show the distribution of the gaze.
-The distribution of the gaze then can be analysed for different user classes (for usability studies), experimental conditions or task based performance (Figures \ref{heatMapGood} and \ref {heatMapBad} \cite{sharma2014how}).
+The distribution of the gaze then can be analysed for different user classes (for usability studies), experimental conditions or task based performance (Figure \ref{heatMap}  \cite{sharma2014how}).
 The mathematical details about how to create the heat maps can be found in \cite{duchowski2007eye}.
@@
     \centering
-    \includegraphics[width=0.9\linewidth]{heat-map-good-ex}
-    \caption{Example heat map for a MOOC student who performed well in the posttest.
-    source: \cite{sharma2014how}}
-    \label{heatMapGood}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.9\linewidth]{heat-map-bad-ex}
-    \caption{Example heat map for a MOOC student who performed poor in the posttest.
-    source: source: \cite{sharma2014how}}
-    \label{heatMapBad}
+    \includegraphics[width=\linewidth]{heat-map}
+    \caption{Left : Example heat map for a MOOC student who performed poor in the posttest. Right: Example heat map for a MOOC student who performed well in the posttest. Source: \cite{sharma2014how}}
+    \label{heatMap}
 \end{figure}
@@
 
+The main challenge with the mobile eye-tracking is that one of the target and the observer is moving, sometimes both are moving.
+This sometimes results in having partial target in the field of view of the observer.
+Hence, there is a methodological problem to solve, which is "how to track the target when it is partially out of sight?" To accomplish this we need to put fiducial markers in the scene or extract some salient features of the target which make it easy to automatically locate the gaze pointer on the target and/or the scene.
 There are several use cases of mobile eye-tracking, we categorise them in following three categories:
@@
 \begin{enumerate}
-\item Moving target, stationary observer
-\item Stationary target, moving observer
-\item Moving target, moving observer
+\item Moving target, stationary observer: in these cases, putting fiducial markers or detecting salient features on the target and the scene is necessary to recreate the true scene while analysing the gaze data.
+\item Stationary target, moving observer: in these cases a three dimensional model of the target can be of great aid when it comes to locating where the observer was looking on the target.
+The 3D model of the target then be divided into different planes of interest (instead of AOIs) and this makes the gaze analysis easy.
+\item Moving target, moving observer: this is the most complicated use case in terms of data analysis and re-localisation of the gaze pointer on the scene.
+The complexity of both these tasks is dependent on the relative motion of the target and the observer.
+Some mobile eye-trackers are equipped with infrared sensors.
+If we put infrared emitting diodes in the scene and on the target, it will help in locating the gaze pointer when both the target and observer are moving.
 \end{enumerate}
-
-Next, we present an example of one of the use cases of mobile eye-tracking.
 
@@
 We propose to use the mobile eye trackers to be able to have our participants
-freely move on the experiment site.This is the reason we used fiducial-markers
-on the maze we used in the experiment so that we can reconstruct the whole maze
+freely move on the experiment site. We used fiducial-markers
+on the playground we used in the experiment so that we can reconstruct the whole maze
 even if only a part of it is the visual field of the participant.

### 2014-10-03 paper.tex
small position cane in 5.3
updated api image

@@
 \item Saccades and transitions: Two fixations are connected by a saccade.
-Saccades are the sudden variations in the eye-movements.
-There are two main ways to analyse saccades: 1) saccade lengths are indicative of the amount of change in the attention; and 2) the two ends of a saccade denote a transition between two areas of scene/screen.
+Saccades are the sudden variations in the eye-movements (Figure \ref{aoi}).
+There are two main ways to analyse saccades: 1) saccade lengths are indicative of the amount of change in the attention; and 2) the two ends of a saccade denote a transition between two areas of scene/screen .
 
@@
 These AOIs are usually based on the hypotheses of the experiment.
-For example, if in a usability study of a phone advertisement \footnote{http://eyetracking.com.ua/eng/visualization/12.html} (Figure \ref{aoi}) the screen can divided into the advertisement model, the object and the caption.
+For example, if in a usability study of a phone advertisement (Figure \ref{aoi}) the screen can divided into the advertisement model, the object and the caption.
 Once the screen has been divided into AOIs, we can compare the gaze distribution for different users and /or different experimental conditions.
@@
     \centering
-    \includegraphics[width=0.4\linewidth]{nokia.jpg}
-    \caption{Example of dividing a screen in Areas of interest. Source: http://eyetracking.com.ua/eng/visualization/12.html}
+    \includegraphics[width=\linewidth]{scanpathVars}
+    \caption{Example of dividing a screen in Areas of interest and the saccades 
+    (lines). Source: \cite{sharma2014how}}
     \label{aoi}
@@
 
+\vspace{1cm}
 \subsection{Participants}

### 2014-10-03 paper.tex
updated section 4.2

@@
 These AOIs are usually based on the hypotheses of the experiment.
-For example, if in a usability study of a phone advertisement (Figure \ref{aoi}) the screen can divided into the advertisement model, the object and the caption.
+For example, if in a study with Massive Open Online Courses (MOOCs) (Figure \ref{aoi}) the screen can divided into various lines in the video lecture of the MOOC.
 Once the screen has been divided into AOIs, we can compare the gaze distribution for different users and /or different experimental conditions.

### 2014-10-03 paper.tex
updated figure 1
changes in section 1 and 4

@@
 \graphicspath{{figures/}}
-
+\usepackage{amsthm}
 \usepackage{booktabs}
@@
 for eye-tracking data are first exhaustively presented, with an emphasis on
-those we believe relevant to robotics. We then report on a study involving the
-educational robot Thymio II~\cite{riedo2012two} with 52 participants: the
+those we believe relevant to robotics. We then report on a study involving an
+educational robot with 52 participants: the
 students have to explain a pre-programmed behaviour of the robot with or without
@@
 Evaluation of HRI is mostly done through qualitative questionnaires and
-qualitative data (interaction videos, interviews for example). The physiological
-measurements such as eye tracking being precise, pertinent and portable at the
-same time provides an added value to the researcher.  Eye-tracking data is of
-high temporal precision as compared to some of the physiological data sources
-such as fMRI or other biometric devices used to measure the palpitation and the
-body temperature. The eye tracking devices are portable enough as opposed to the
-bulky apparatus used in fMRI~\cite{rosenthal2013neural}. Eye tracking data
-provides more direct access to the users' attention than other portable and
-physiological data sources such as EEG and wristbands measuring skin conductance
-and pulse rate; this makes eye-tracking data a pertinent source to measure
-attention.
+qualitative data (interaction videos, interviews for example).
+There are some physiological devices as well.
+For example fMRI, EEG, eye-tracking and skin conductance.
+These measures have been used in the research where the researchers attempt to get a proxy for the users' attention.
 
-The prime advantage of using mobile eye-tracking is that the users' interaction
-with the robot can still be ecologically valid. On the other hand, using fMRI
-for evaluating HRI reduces the interaction to a video of the robot
-only~\cite{rosenthal2013neural}.
+Functional MRI (fMRI) data gives a direct access to the brain signals and so does EEG data.
+The main disadvantage of using the fMRI data to assess the human robot interaction situations is that the apparatus is bulky and the interaction is limited to a few videos only.
+This is not the case with EEG but EEG has too much noise in the data due to involuntary actions of the human  body, which makes the assessment of the behaviour difficult.
+The devices that measure skin conductance and the pulse rate are  small and portable; but the relation between the data they collect and the user's behaviour is questionable as the skin conductance and pulse rate measures are highly environment dependent.
 
-Another advantage of using mobile eye-tracking to assess HRI situations, is that
-the data provides direct and noise free access to the users' attention. While in
-other physiological measures for attention, such as EEG, the data has a lot of
-noise and the relation to the attention is very task-specific.
+The prime advantage of using mobile eye-tracking is that the users' interaction with the robot can still be ecologically valid.
+On the other hand, using fMRI for evaluating HRI reduces the interaction to a video of the robot only~\cite{rosenthal2013neural}.
+Another advantage of using mobile eye-tracking to assess HRI situations, is that the data provides direct and noise free access to the users' attention.
+While in other physiological measures for attention, such as EEG, the data has a lot of noise and the relation to the attention is  task-specific.
+
+Eye tracking being precise, pertinent and portable at the same time provides an added value to the researcher.
+Eye-tracking data is of high temporal precision as compared to some of the physiological data sources such as fMRI or other biometric devices used to measure the palpitation and the body temperature.
+The eye tracking devices are portable enough as opposed to the bulky apparatus used in fMRI~\cite{rosenthal2013neural}.
+Eye tracking data provides more direct access to the users' attention than other portable and physiological data sources such as EEG and wristbands measuring skin conductance and pulse rate; this makes eye-tracking data a pertinent source to measure attention.
 
@@
 data acquisition is a better trade-off between the ecological validity of the
-experiment (as there cannot be an interaction with the robot fMRI data
+experiment (as there cannot be an interaction with the robot during fMRI data
 acquisition) and the precision of the data stream (wristbands for measuring the
@@
 applications: eye-tracking as an \emph{interaction modality} and eye-tracking as
-an \emph{interaction assessment} tool. It appears that the literature in both
-these fields is scarce.
+an \emph{interaction assessment} tool. It appears that the literature for both
+these applications is scarce.
 
@@
 
-\subsection{Gaze patterns and Expertise/Task based performance}
+There are two main fields of research in eye-tracking with the human users.
+First, the attempts to correlate the gaze patterns of participants in different expertise levels and/or different task based performance levels.
+Second, the  attempts to analyse  the socio-cognitive constructs in joint tasks like collaboration quality and collaborative performance.
+
+\paragraph{Gaze patterns and Expertise/Task based performance}
 
 Several scholars related gaze patterns with level of expertise.
-\cite{hasse2012measure} in an air traffic-monitoring task found out that the
-experts looked less at the scenario-specific information than novices.
+In an air traffic-monitoring task, \cite{hasse2012measure}  found out that the
+experts looked \emph{less} at the scenario-specific information than novices.
 \cite{eivazi2012gaze, law2004eye, tien2010measuring} studied the effect of
@@
 
-\subsection{Gaze patterns and Collaborative performance}
+\paragraph{Gaze patterns and Collaborative performance}
 
@@
 performance in collaborative settings. As a measure of joint attention in
-collaborative settings  \cite{richardson2007art} proposed gaze recurrence
+collaborative settings  \cite{richardson2007art} proposed \emph{gaze cross recurrence}
 between the collaborators and showed it to be correlated with the collaboration
@@
 parts in the program while poor performing teams have equal distribution of gaze
-on different parts of the program during similar phase of the task.  Thus we see
-that previous research provides insights about the relationship between the gaze
+on different parts of the program during similar phase of the task.
+
+We see that previous research provides insights about the relationship between the gaze
 patterns and the behavioural and task-based performance indicators in diverse
-scenarios.
+scenarios including both the individual users and in collaborative settings. We believe that the application of eye-tracking methods can provide useful insights about human-robot interaction.
 
@@
 
-\section{State of Eye Tracking in Human-Robot Interaction}
+\paragraph{State of Eye Tracking in Human-Robot Interaction}
 \label{et_robotics}
 
-The usage of eye-tracking methods in HRI is very sparse. It must be noted that
-to our best knowledge only very few attempts to use eye-tracking as an
-interaction modality or as an interaction assessment technique in HRI.
+The usage of eye-tracking methods in HRI is  sparse.
+It must be noted that to our best knowledge there are only a few attempts where the experiments have been conducted to use eye-tracking as an interaction modality or as an interaction assessment technique in HRI.
 
-\subsection{Eye Tracking as an Interaction Modality}
+\paragraph{Eye Tracking as an Interaction Modality}
 
-To guide the motion of a robot \cite{bhuiyan2004tracking} used real time  gaze
-data of a human user. The users were able to provide the visual and geometrical
-motion information to the robot by moving their eyes in different parts of the
-human-robot interface.
+To guide the motion of a robot \cite{bhuiyan2004tracking} used real time  gaze data of a human user.
+The users were able to provide the visual and geometrical motion information to the robot by moving their eyes in different parts of the human-robot interface.
 
-\subsection{Eye Tracking as a tool to Assess Interaction Algorithms}
+\paragraph{Eye Tracking as a tool to Assess Interaction Algorithms}
 
-To evaluate the effectiveness of the motion planning algorithm for a robot
-\cite{dehais2011physiological} used eye-tracking techniques. In an object
-hand-over task between a robot and a human, the authors compared various motion
-planning algorithms based on the gaze of the human.
+To evaluate the effectiveness of the motion planning algorithm for a robot \cite{dehais2011physiological} used eye-tracking techniques.
+In an object hand-over task between a robot and a human, the authors compared various motion planning algorithms based on the gaze of the human.
 
-\subsection{Eye Tracking as a tool to Assess Joint Attention}
+\paragraph{Eye Tracking as a tool to Assess Joint Attention}
 
-In an eye-tracking study, in the context of human robot interaction,
-\cite{staudte2009visual} found that when the robot provides a matching visual
-and verbal reference to an object the participants were more likely to look at
-the correct objects. This result was consistent irrespectively of the ambiguity
-of the situation. The video based interaction modality was used by the authors.
-This constraints the  interaction of the human-robot dyad to just a video.
-However, the stimulus (video) for eye-tracking provides strong contrast and a
-good control for experimental conditions.
+In an eye-tracking study, in the context of human robot interaction, \cite{staudte2009visual} found that when the robot provides a matching visual and verbal reference to an object the participants were more likely to look at the correct objects.
+This result was consistent irrespectively of the ambiguity of the situation.
+The authors did not conduct a face to face interaction between the human and the robot instead they used the videos of robot performing the disambiguation task.This constraints the  interaction of the human-robot dyad to just a video.However, the stimulus (video) for eye-tracking provides strong contrast and a good control for experimental conditions.
 
@@
 \section{Method description}
+
+In this section, we present an exhaustive summary of eye-tracking apparatus, setups (especially focusing on mobile eye-tracking), analysis methods and use cases for mobile eye-tracking.
+
 \label{method}
@@
 \subsection{Eye-tracking}
-First, we introduce the basic eye-tracking setups, technical steps in mobile eye-tracking and different use cases of mobile eye-tracking.
+First, we introduce the basic eye-tracking setups and technical steps in mobile eye-tracking and different use cases of mobile eye-tracking.
 
@@
 
-Most eye trackers work by projecting infrared light on the pupil and measuring the reflection with one or more cameras. . Following are the typical setups for the eye-trackers used in research:
+Most eye trackers work by projecting infrared light on the pupil and measuring the reflection with one or more cameras. Following are the typical setups for the eye-trackers used in research:
 
-\begin{enumerate}
-\item Stationary: The stationary eye-trackers are widely used for the controlled laboratory experiments.
+ \textbf {Stationary:} The stationary eye-trackers are widely used for the controlled laboratory experiments.
 These eye-trackers have a separate eye-tracking device (camera, infrared source and microprocessor) and a monitor or a monitor embedded with different parts  of the eye-tracking devices.
@@
 
-\item Mobile: Mobile eye-trackers are useful to conduct more ecologically valid and naturalistic experiments.
+\textbf {Mobile}: Mobile eye-trackers are useful to conduct more ecologically valid and naturalistic experiments.
 These eye-trackers have a scene camera in the front to record the visual field of the participants.
@@
 
-\item Dual eye-tracking: Dual eye-tracking requires synchronisation of two eye-trackers, so that the researchers can record the gaze data for a pair of collaborators without any lag (as the clocks of two systems can not be perfectly synchronised).
+ \textbf {Dual eye-tracking}: Dual eye-tracking requires synchronisation of two eye-trackers, so that the researchers can record the gaze data for a pair of collaborators without any lag (as the clocks of two systems can not be perfectly synchronised).
 \cite{nussli2011dual} explored and compared different ways to synchronise two eye-trackers.
-
-\end {enumerate}
 
@@
 
-Mobile eye-tracking requires more caution during data collection, as the heads and the bodies (in some cases) of the participants are free to move. We list the main challenges here:
-
-\begin{enumerate}
-\item Calibration: The calibration step of the mobile eye-trackers is crucial, as the head of the participant is always moving. The experimenter needs to make sure that while calibrating 
-\item Recording Scene and gaze: The mobile eye-trackers record the scene video and the gaze pointer information is given in the coordinate system of this video.
-\item Localisation of gaze pointer:  Using mobile eye tracker poses a technical challenge to automatically locate where the participants are actually looking.
+Mobile eye-tracking requires more caution during data collection, as the heads and the bodies (in some cases) of the participants are free to move.
+The calibration step of the mobile eye-trackers is crucial, as the head of the participant is always moving.
+The experimenter needs to make sure that while calibrating the head of the participant have minimal movement.The mobile eye-trackers record the scene video and the gaze pointer information is given in the coordinate system of this video.
+Hence localisation of gaze pointer in terms of real world is necessary.
+Using mobile eye tracker poses a technical challenge to automatically locate where the participants are actually looking.
 This is not a trivial task as the visual stimulus for participants is changing with every bit of motion of their head.
-
-\end {enumerate}
+To solve this problem we need to put markers or patterns in the scene.
 
@@
 
-\begin{enumerate}
-\item Fixations: The most common form of eye-tracking data aggregation are the fixations.
+Eye-trackers have a high data rate which translates to the fact that from a small duration of interaction the collected data can be  overwhelming in size.
+We present a few ways to aggregate the data which are mostly used in eye-tracking research and are useful for analysing behaviour.
+
+ \textbf {Fixations}: The most common form of eye-tracking data aggregation are the fixations.
 Fixations depict the periods in the user's observation when the user attends a relatively small part of the visual stimulus for a relatively longer period of time.
 The various fixation detection algorithms are summarised in~\cite{duchowski2007eye}.
+Fixation durations on a specific area of the screen are directly associated with the attentive period for that specific area.
+Also the distribution of the fixations over the scene tells us that where and how much the participants were paying attention.
 
-\item Saccades and transitions: Two fixations are connected by a saccade.
+ \textbf {Saccades and transitions}: Two fixations are connected by a saccade.
 Saccades are the sudden variations in the eye-movements (Figure \ref{aoi}).
@@
 
-\item Smooth Pursuit: This is a special type of event that gives insights about continuously following a moving object in the field of view.
+ \textbf {Smooth Pursuit}: This is a special type of event that gives insights about continuously following a moving object in the field of view.
 These events are analysed for their durations, especially when there is a moving target that the participants need to observe.
 
-\item Areas of Interest (AOI):  AOIs are those parts of the scene/screen that the experimenter wants to analyse the interaction (with the interface or with another user / robot).
+ \textbf {Areas of Interest (AOI)}:  AOIs are those parts of the scene/screen that the experimenter wants to analyse the interaction (with the interface or with another user / robot).
 These AOIs are usually based on the hypotheses of the experiment.
@@
     \includegraphics[width=\linewidth]{scanpathVars}
-    \caption{Example of dividing a screen in Areas of interest and the saccades 
-    (lines). Source: \cite{sharma2014how}}
+    \caption{Example of dividing a screen in Areas of interest and the saccades (red lines). Source: \cite{sharma2014how}}
     \label{aoi}
@@
 
-\item Heat maps: Heat maps are classical data visualisation tools.
+ \textbf {Heat maps}: Heat maps are classical data visualisation tools.
 In terms of visualising eye-tracking data the heat maps show the distribution of the gaze.
-The distribution of the gaze then can be analysed for different user classes (for usability studies), experimental conditions or task based performance (Figure \ref{heatMap}  \cite{sharma2014how}).
+The distribution of the gaze then can be analysed for different user classes (for usability studies), experimental conditions or task based performance (Figure \ref{heatMap} ).
 The mathematical details about how to create the heat maps can be found in \cite{duchowski2007eye}.
@@
 
-\end {enumerate}
-
 \subsection{Analysing social behaviour}
@@
 
-\begin{enumerate}
-
-\item Joint attention: Maintaining common grounds among the collaborators is key to success during collaborators.
+ \textbf {Joint attention}: Maintaining common grounds among the collaborators is key to success during collaboration.
 This is achieved via references to the objects visible by both the participants in a pair.
-There are two events that create a moment of joint attention: 1) eye-voice span \cite{griffin2000eyes}: the referencing partner looks at the referred site before referring to it; and 2) voice-eye span \cite{allopenna1998tracking}: after the reference the non- referencing partner looks at the referred site.
+There are two events that create a moment of joint attention: 1) eye-voice span \cite{griffin2000eyes}: the referencing partner looks at the referred site before referring to it; and 2) voice-eye span \cite{allopenna1998tracking}: after the reference the non-referencing partner looks at the referred site.
 These moments of joint attention help them to create the common ground in the first place and further, they help in maintaining the common ground.
-The time lag between the speaker's gaze and listener's gaze at the referred object is called gaze cross recurrence \cite{richardson2007art}.
+The time lag between the speaker's gaze and listener's gaze at the referred object is called \emph{gaze cross recurrence} \cite{richardson2007art}.
 The gaze cross recurrence has been shown to be correlated with the collaboration quality and joint task performance \cite{nussli2011dual}.
 
-\item Interaction episodes: Apart from moments of joint attention, collaboration contains sequence of actions and communicative moves.
+ \textbf {Interaction episodes:} Apart from moments of joint attention, collaboration contains sequence of actions and communicative moves.
 To build a model of the interaction quality, it is essential to put temporal markers in the flow of interaction.
-\cite{sharma2012gaze} defined the segments of interaction by detecting stable (looking at a small set of objects) and together (looking at the same set of objects) moments.
-Simply put,
-for automatic assessment of quality of interaction, we need to find out how to automatically segment the interaction based on gaze data.
+\cite{sharma2012gaze} defined the segments of interaction by detecting \emph{stable} (looking at a small set of objects) and \emph{together} (looking at the same set of objects) moments.
+Simply put, for automatic assessment of quality of interaction, we need to automatically segment the interaction based on gaze data.
 It is important to keep in mind that different level of gaze aggregation can help in finding evidences for different granularities of task decomposition.
-\end{enumerate}
 
@@
 
-The main challenge with the mobile eye-tracking is that one of the target and the observer is moving, sometimes both are moving.
-This sometimes results in having partial target in the field of view of the observer.
-Hence, there is a methodological problem to solve, which is "how to track the target when it is partially out of sight?" To accomplish this we need to put fiducial markers in the scene or extract some salient features of the target which make it easy to automatically locate the gaze pointer on the target and/or the scene.
-There are several use cases of mobile eye-tracking, we categorise them in following three categories:
+Mobile eye-tracking is  useful when the target and/or the observer is moving, or the experimental setup requires one or both of them to move.
+For example, in child-robot interaction situations, we can use mobile eye-trackers to see how much the child look at the robot and what are the actions robot does which attract most of the child's attention.
+Also in the case of robots designed for the elderly and demented people we could assess the effects of robots' actions on the gaze of the users.
 
-\begin{enumerate}
-\item Moving target, stationary observer: in these cases, putting fiducial markers or detecting salient features on the target and the scene is necessary to recreate the true scene while analysing the gaze data.
-\item Stationary target, moving observer: in these cases a three dimensional model of the target can be of great aid when it comes to locating where the observer was looking on the target.
-The 3D model of the target then be divided into different planes of interest (instead of AOIs) and this makes the gaze analysis easy.
-\item Moving target, moving observer: this is the most complicated use case in terms of data analysis and re-localisation of the gaze pointer on the scene.
-The complexity of both these tasks is dependent on the relative motion of the target and the observer.
-Some mobile eye-trackers are equipped with infrared sensors.
-If we put infrared emitting diodes in the scene and on the target, it will help in locating the gaze pointer when both the target and observer are moving.
-\end{enumerate}
+Having the target and/or the  observer moving may result in having partial target in the field of view of the observer.
+Hence, there is a methodological problem to solve, which is "how to track the target when it is partially out of sight?" To accomplish this we need to put fiducial markers in the scene or extract some salient features of the target which make it easy to automatically locate the gaze pointer on the target and/or the scene
 
@@
 
-In this section, we present a mobile eye-tracking study with an educational
-robot Thymio II. The study exemplifies one of the use cases of the mobile
-eye-tracking. One part of the target (the robot) was moving, whereas the rest of
-the maze (or playground, figure~\ref{playground}, as we refer to it in the rest
-of this paper) was stationary. The participants were allowed to move but most of
-them remained seated for the duration of the experiment. For the purpose of the
-eye-tracking data analysis, we used the proportions of fixations on different
-area of interest on the playground.
-
-We propose to use the mobile eye trackers to be able to have our participants
-freely move on the experiment site. We used fiducial-markers
-on the playground we used in the experiment so that we can reconstruct the whole maze
-even if only a part of it is the visual field of the participant.
+In this section, we present a mobile eye-tracking study with an educational robot Thymio II \cite{riedo2012two}.
+The study exemplifies one of the use cases of the mobile eye-tracking.
+One part of the target (the robot) was moving, whereas the rest of the maze (or playground, as we refer to it in the rest of this paper) was stationary.
+The participants were allowed to move but most of them remained seated for the duration of the experiment.
+We decided to use the mobile eye trackers to be able to have our participants freely move on the experiment site.
 
@@
 children~\cite{magnenat2012programming, riedo2012two}. Users can interact with
-it via buttons and distance sensors. The robot can display its states via many
+it via buttons and distance sensors. The robot can display its states via 
 LEDs and its motion. We programmed it to show the value of the front IR-sensor
@@
 obstacles and the position of the gaze on the video recorded from the
-eye-tracker. The localisation is made possible by the use of unique fiducial
-markers on the playground. On the right hand side, the observation phase takes
+eye-tracker.  On the right hand side, the observation phase takes
 place and there will be the reference for the black and white obstacles. On the
@@
 us to recreate the whole playground for every frame in the video
-recorded from the eye-tracker's camera (Figure~\ref{expe}).
+recorded from the eye-tracker's camera (Figure~\ref{maze}).
 
-\subsection{Procedure}
+\subsection{Procedure and Participants}
 
-Upon their arrival at the experiment site, the participants signed a consent
-form and answered a small questionnaire about demographics and participant's
-experience with educational robots (this we later consider as expertise). The
-participants were placed in front of the playground (Figure~\ref{expe}) and were
+We recruited 52 participants for the experiment. All of them were
+students from ANONYMOUS, ANONYMOUS. The participants were placed in front of the playground (Figure~\ref{expe}) and were
 equipped with the SMI eye-tracking glasses. The eye-tracker records the gaze
@@
 
-\vspace{1cm}
-\subsection{Participants}
-
-We recruited 52 participants for the experiment. All of them were
-students from École Polytechnique Fédérale de Lausanne, Switzerland.
-Most of them were in their first year undergraduate program (with two
-exceptions). ~The age distribution was narrow, with a mean of 19.7 and a
-standard deviation of 1.97. There were 13 female and 39 male
-participants. In the three experimental conditions, {\sf NONE}, {\sf RANDOM} and
-{\sf TRUE}, there were 18, 17 and 17 participants respectively.
-
 \subsection{Eye-tracking measures}
@@
 
-We measured the distances from the target were measured for all 5 trials. As
-a matter of fact, as soon as the principle of the robot was deemed to be
-understood by the participants, almost all the participants behaved the
-same way. On the first try almost every participant failed and the robot
-turned instantly. So the most significant distance measure was the
-improvement between the first and second trial. It is referred to as
-improvement in the following sections.
+We measured the distances from the target for all 5 trials.
+As soon as the principle of the robot was deemed to be understood by the participants, almost all the participants behaved the same way.
+On the first try almost every participant failed and the robot turned instantly.
+So the most significant distance measure was the
+improvement between the first and second trial. It is referred to as improvement in the next section.
 
@@
 
-\section{Interpreting the Results}
+\section{Results and Interpretation}
 \label{interpretation}
@@
 
-We found no bias for age, gender, expertise, student status or condition
-in respect to the correctness, abstraction and type of mistake made for
-the final answer. Surprisingly there is no correlation between the
-visualisation condition and the correctness or abstraction of the
-answers given. We could not find any anticipation patterns in the
-eye-tracking data. We found some other relation between the different
-measures. We present the results in following subsections.
-
-\subsubsection{Average fixation duration on the robot during observation phase
+\paragraph{Average fixation duration on the robot during observation phase
 vs.~condition}
@@
 
-\subsubsection{First improvement vs.~condition}
+\paragraph{First improvement vs.~condition}
 
@@
 
-\subsubsection{Average fixation duration on the reference side during interaction
+\paragraph{Average fixation duration on the reference side during interaction
 phase vs.~condition}
@@
 
-\subsubsection{First improvement vs number of fixations on reference side}
+\paragraph{First improvement vs number of fixations on reference side}
 
@@
 therefore it may behave differently.
-
-The fact that the participants in the {\sf RANDOM} or {\sf NONE} visualisation
-condition improved more than those with {\sf TRUE} condition is surprising
-(Figure 5). There are two plausible explanations. The first is that
-participants who see the robot in the {\sf TRUE} condition have a stronger
-belief that the robot always behaves the same. They see the LEDs of the
-robot turning on and therefore the robot still works. The ones with {\sf NONE}
-visualisation do not have an indication whether the robot works the same
-way as in the observation phase, and start experimenting earlier. The
-second is that the participants in {\sf TRUE} condition just put the obstacles
-out of detection range, because they could see different display
-information and concluded therefore it may behave differently.
 

### 2014-10-03 paper.tex
Polishing conclusion

@@
 
-The task that we have presented was initially motivated by those two questions:
+The robotic task that we have just presented was initially motivated by those
+two questions:
 
 \begin{enumerate}
-    \item Can we characterise the participants' behaviours that
+    \item Can we \emph{characterise} the participants' behaviours that
         lead to good performance during the interaction? In particular, do
-        we observe any anticipation patterns for the good performers?
+        we observe any higher cognitive skills like anticipation patterns for
+        the good performers?
 
-    \item How does visual cue affects the performance of the participants?
+    \item How do visual cues affect the performance of the participants?
 
@@
 
-The task was performance-oriented and yet we were interested in accessing and
-understanding the cognitive mechanisms at stake during the interaction: where do
-participants look when they want to understand a robot behaviour? Does
-\emph{anticipation} reflect understanding? How the robot's design impact the
-interaction?
+We indeed were interested in accessing and understanding the cognitive
+mechanisms at stake during the interaction: where do participants look when they
+want to understand a robot behaviour? Does \emph{anticipation} for instance
+reflect understanding? How the robot's design impact the interaction? These kind
+of questions are common in HRI, and ee believe that mobile eye-tracking, as a
+relatively non-invasive yet accurate (both spatially and temporally) biometric
+measurement, is a valuable tool to investigate them in ecologically
+valid environments.
 
-We believe that mobile eye-tracking, as a relatively non-invasive yet accurate
-(both spatially and temporally) biometric measurement, is a key tool to
-investigate this kind of questions in ecologically valid environments.
-
-In that regard, we identify three main strengths of eye-tracking. First,
-eye-tracking introduce less experimental bias: mobile eye-tracker are
-non-invasive and lightweight. Combined with mobile recording units, they do not
-put any constraints on participant movements, contrary to traditional techniques
-like video recording. Also, contrary to questionnaires or interview-based
-protocol where the experimenter active role may influence the assessment,
-eye-tracker are easy to ``forget about'' for the participants.
+We identify three main strengths of eye-tracking. First, eye-tracking introduces
+less experimental bias: mobile eye-tracker are non-invasive and lightweight.
+Combined with mobile recording units, they do not put any constraints on
+participant movements, contrary to traditional techniques like video recording.
+Also, contrary to questionnaires or interview-based protocols where the
+experimenter's active role may influence the participants' answers, eye-trackers
+are easy to ``forget about'' for the participants.
 
@@
 attentional focus~\cite{sharma2014withmeness} (both spatially -- where does the
-subject look at -- and temporally -- where does the subject's attention stays).
-Importantly, this information leads to a fine-grained measure of
+subject look at -- and temporally -- where does the subject's attention remain).
+Importantly, this information can be implicitly interpreted as a fine-grained measure of
 \emph{engagement}.  Also, the good temporal resolution of eye-trackers allows
-for the accurate study of the \emph{dynamics} of attention: what are the
-attentional patterns of the subject during the interaction.
+for the accurate study of the \emph{dynamics} of attention, including possible
+\emph{attentional patterns} of the subject during the interaction.
 
-Third, it has been showed in literature that eye-tracking can provide an
+Third, it has been shown in literature that eye-tracking can provide an
 effective measure of higher socio-cognitive behaviours: it can be used as a
@@
 
-Besides, mobile eye-tracking come with an additional cost. As
-we mentioned earlier, the automatic localisation of the gaze pointer on
-the visual stimulus is not a trivial task. In our study, we relied on a 
-number of fiducial markers to the playground, but they were reported as
-distractive by the participants. More complex computer vision tools (object
-tracking) can alleviate the need for such markers, but it certainly requires
-significant pre-processing prior to data analysis.
+Besides, mobile eye-tracking come with an additional cost. As we mentioned
+earlier, the automatic localisation of the gaze pointer on the visual stimulus
+is not a trivial task. In our study, we relied on a number of fiducial markers
+to the playground, but they were reported as distractive by the participants.
+More complex computer vision tools (like object tracking) can alleviate the need
+for such markers, but it certainly requires significant pre-processing prior to
+data analysis.
 

### 2014-10-03 paper.tex
Removed amsthm package + fixed wrong ref

@@
 \graphicspath{{figures/}}
-\usepackage{amsthm}
+%\usepackage{amsthm}
 \usepackage{booktabs}
@@
 us to recreate the whole playground for every frame in the video
-recorded from the eye-tracker's camera (Figure~\ref{maze}).
+recorded from the eye-tracker's camera (Figure~\ref{playground}).
 

### 2014-10-03 paper.tex
Updated section 5

@@
 Average fixation on the reference side: The main area (right hand side
-of figure 2) in the observation phase is treated as the reference side
+of figure \ref{playground}) in the observation phase is treated as the reference side
 in the interaction phase. The rationale behind keeping the lines drawn
@@
 As soon as the principle of the robot was deemed to be understood by the participants, almost all the participants behaved the same way.
-On the first try almost every participant failed and the robot turned instantly.
+On the first try almost every participant failed with the robot turning instantly.
 So the most significant distance measure was the
@@
 
+In this section, we give some of the results form the study which illustrate how fixations can be used to analyse the behaviours during the human-robot interaction and the cognitive constructs can be supported with the results.
+
 \subsection{Results}
+
+First, we show how fixation durations can be used to compare the experimental conditions and the task based performance levels.
 
@@
 (Figure~\ref{res1}) is significantly more in {\sf TRUE} and {\sf RANDOM} condition than in
-the {\sf NONE} condition ($F[2,49]=3.68$, p = .03). This depicts that the
+the {\sf NONE} condition ($F[2,49]=3.68$, p = .03). This shows that the
 sensor data visualisation has an effect on the users' attention.
@@
 
-There is a significant negative correlation between the number of
+Now we show how we can use the fixation counts on different areas of interest to analyse the different task based performance levels. There is a significant negative correlation between the number of
 fixations on the reference side (Figure~\ref{res4}) during the interaction phase
@@
 
-We present an exemplar eye-tracking study in the context of human-robot
-interaction within an educational setting. In this section we give an example of
-"how to interpret the eye-tracking results". The fact that participants have
+The fact that participants have
 higher average fixation duration on the robot during the observation phase in

### 2014-10-03 paper.tex
Balance columns on last page
updated section 5.2

@@
 effect during the interaction.
+It is important to highlight the fact that the previous two interpretations combine the behaviour of the participants, the experimental condition and the gaze measures.
+Thus eye-tracking provide a strong tool to form and verify cognitive hypotheses to interpret the social behaviour in human-robot interaction.
 
+We can also have a similar interpretation from the relation between the fixation counts and the first improvement. The fact that there is a negative correlation  between the number of
+fixations on the reference side (Figure~\ref{res4}) during the interaction phase
+and the first Improvement also reflects that those participants who had higher belief in their initial mental models did not look at the reference side in the interaction phase and failed in the first trial.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 reflect understanding? How the robot's design impact the interaction? These kind
-of questions are common in HRI, and ee believe that mobile eye-tracking, as a
+of questions are common in HRI, and we believe that mobile eye-tracking, as a
 relatively non-invasive yet accurate (both spatially and temporally) biometric
